### 2025-05-01 tex/manuscript.tex
Feat: Complete datasets, initial manuscript

\documentclass[11pt]{article}
\usepackage[toc,page]{appendix}
\RequirePackage{fix-cm}
\usepackage[utf8]{inputenc}
\usepackage[margin=1.5in]{geometry}
\usepackage[bottom, flushmargin]{footmisc}
\setlength{\footnotesep}{\baselineskip} % space between footnotes 
\setlength{\parindent}{0in} % space at start of paragraph
\setlength{\parskip}{0.14in} % space between paragraphs
\linespread{1.25}
\usepackage{titlesec}
\titlespacing\section{0pt}{0.21in}{0.03in}
\titlespacing\subsection{0pt}{0.21in}{0.01in}
\titlespacing\subsubsection{0pt}{0.21in}{0in}
\usepackage{marginnote}
\newcommand{\marnum}[1]{\reversemarginpar \marginnote{#1}[0.14in]}

% bibliography-related packages
\usepackage[superscript]{cite}
\bibliographystyle{unsrt}

% lists
\usepackage{enumitem} 
\newcommand{\bulletlabel}{\raisebox{0.2ex}{\small$\bullet$}}
\newlist{enumbul}{enumerate}{6}
\setlist[enumbul]{label=\bulletlabel, topsep=0pt, leftmargin=0.3in, rightmargin=0.3in}
\newlist{enumar}{enumerate}{6}
\setlist[enumar]{label=\arabic*$)$,topsep=0pt, leftmargin=0.3in, rightmargin=0.3in}

% packages vital for various things
\usepackage{hyperref}
\usepackage{comment} % commenting out a large chunk
\usepackage{enumitem} % lists
\usepackage{graphicx,nicefrac} % graphics, especially external ones
\graphicspath{ {dataviz/} }
\usepackage{amsmath} % writing math
\usepackage{amssymb} % writing symbols
\usepackage{amsthm}
\usepackage{bm}
\usepackage{float}
\usepackage{mathtools}
\usepackage{bigints}

% colors
\usepackage{tcolorbox}
\usepackage{color} % colors
\usepackage{xcolor, colortbl} % more control over colors
\newcommand{\red}[1]{\color{red}#1\color{black}}
\newcommand{\green}[1]{\color{green!80!black}#1\color{black}}
\newcommand{\blue}[1]{\color{blue}#1\color{black}}
\newcommand{\gray}[1]{\color{gray!80!black}#1\color{black}}
\newcommand{\black}[1]{\color{black}#1\color{black}}

\hypersetup{
	colorlinks,
	linkcolor=black, %internal links
	urlcolor=cyan,  % URLs
	citecolor= red, % references
	breaklinks=true
}

% for use in tables
\usepackage{multirow}
\usepackage{multicol}
\usepackage{array}
\usepackage{booktabs}
\newcommand\bstrut{\rule{0pt}{2.5ex}} % space before row
\newcommand\astrut{\rule[-1.25ex]{0pt}{0pt}} % space after row
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

%miscellaneous
\newcommand{\ansm}[1]{\text{\framebox{\ensuremath{#1}}}}
\newcommand{\anst}[1]{\text{\framebox{#1}}}
\newcommand{\ie}[1][]{\textit{i.e.\ }#1}
\newcommand{\eg}[1][]{\textit{e.g.\ }#1}
\newcommand\pspace {\\[0.07in]}
\newcommand\ppspace {\\[0.14in]}
\newcommand{\logsep}{\begin{center}---------------\end{center}}

\def\highlight#1#2{
	\begin{centering}

		\vspace{1.2ex}
		\begin{minipage}{0.8\linewidth}
			\begin{tcolorbox}[boxsep = 3.3pt, boxrule=0.4pt, colback = white, colbacktitle=white, coltitle = black, colframe= black, title=\centering \textbf{#1}]
				\centering
				#2
			\end{tcolorbox}
		\end{minipage}
		\vspace{1.2ex}

	\end{centering}
}

\begin{document}
\pagenumbering{gobble}

\phantom{Thevesh}

\vfill

\begin{center}
	\begin{minipage}{0.88\linewidth}
		\begin{center}
			\LARGE
			The Malaysian Election Corpus: Federal and State Election Results from 1955 to the Present\\[0.21in]
			\Large
			Thevesh Thevananthan\\[0.15in]  % ← Author name inserted here
		\end{center}
		\large 
		Lorem ipsum dolor sit amet, consectetur adipiscing elit. Sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
	\end{minipage}
\end{center}

\vfill

\phantom{Word Count:}

\newpage
\pagenumbering{arabic}

\section*{Background \& Summary}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex\cite{ge00report} ea commodo consequat.

\section*{Methods}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.

\section*{Data Records}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.

\section*{Technical Validation}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.

\section*{Usage Notes}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.

\section*{Code Availability}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.

\newpage

% this section generates reference
\begingroup
\raggedright
\let\oldthebibliography\thebibliography
\bibliography{mybib}
\endgroup
\section*{Author Contributions}
TT conceived, designed, and carried out all aspects of this study, including data collection, data curation, analysis, and manuscript preparation.

\section*{Competing Interests}
The author declares no competing interests. The author is not affiliated with any political party, or any private or non-governmental organization that has a vested interest in the outcome of Malaysian elections.

\section*{Acknowledgements}
This work did not receive any specific funding. We thank Rosmadi Fauzi and Zulkanain Abdul Rahman for their helpful feedback on the dataset and manuscript. We also gratefully acknowledge Nimesha Thevananthan for their assistance with data collection, as well as Danesh Prakash Chacko of Tindak Malaysia for providing valuable insights and assisting with filling gaps in the data, particularly for Sabah in 1971. Finally, we thank the Election Commission (EC) of Malaysia for granting access to well-maintained physical records of historical election results stored in the library at its headquarters.

\end{document}

### 2025-05-01 compile.py

@@ -1,0 +1,134 @@
+import pandas as pd
+import numpy as np
+import json as j
+
+from helper import get_states, write_csv_parquet
+
+dates = j.load(open('src-data/dates_master.json'))
+STATES = get_states(my=1)
+
+
+def compile_ballots():
+    df = pd.DataFrame()
+    for s in STATES + ['PRK']:
+        if 'W.P.' in s: continue
+
+        BLIM = 0 if s in ['Malaysia','PRK'] else 1
+        ULIM = 1 if s == 'PRK' else 13 if s == 'Sarawak' else 15 if s == 'Sabah' else 16
+        TYPE = 'federal' if s == 'Malaysia' else 'prk' if s == 'PRK' else 'state'
+        NAME = 'GE' if s == 'Malaysia' else 'BY-ELECTION' if s == 'PRK' else 'SE'
+
+        for e in range(BLIM,ULIM):
+
+            FILENAME = \
+                f'ge{e:02d}_ballots.csv' if TYPE == 'federal' else \
+                'prk_ballots.csv' if TYPE == 'prk' else \
+                f"{s.lower().replace(' ','')}_se{e:02d}_ballots.csv"
+            tf = pd.read_csv(f'src-data/{TYPE}/{FILENAME}').rename(columns={'parlimen':'seat','dun':'seat'})
+
+            COL_ORI = [x for x in tf.columns if x not in ['date','election']]
+            tf['election'] = f'{NAME}-{e:02d}' if TYPE != 'prk' else NAME
+            if TYPE != 'prk': tf['date'] = dates[s][str(e)] 
+            tf = tf[['date','election'] + COL_ORI]
+            
+            # Generate total valid votes for each seat, and then derive percentage of votes for each candidate
+            sf = tf[['seat','votes']].groupby('seat').sum().reset_index().rename(columns={'votes':'votes_perc'})
+            tf = pd.merge(tf,sf,on='seat',how='left')
+            tf.votes_perc = tf.votes/tf.votes_perc * 100
+
+            # Classify results
+            tf['result'] = 'lost'
+            tf.loc[tf.votes_perc < 12.5, 'result'] = 'lost_deposit'
+            tf['nameseat'] = tf.name + tf.seat
+            sf = tf[['nameseat','seat','votes']].sort_values(by=['seat','votes']).drop_duplicates(subset='seat',keep='last')
[…]

### 2025-05-01 helper.py

@@ -1,0 +1,89 @@
+import pandas as pd
+import re
+
+import boto3
+from datetime import date,timedelta, datetime
+import time
+
+TOKEN_API_S3 = ('YOUR_ACCESS_KEY', 'YOUR_SECRET_KEY')
+
+
+# upload file to bucket (S3)
+def upload_s3(bucket_name=None, source_file_name=None, cloud_file_name=None):
+    if not cloud_file_name: cloud_file_name = source_file_name
+    try:
+        time_start_temp = time.time()
+        s3 = boto3.client(
+            's3',
+            aws_access_key_id=TOKEN_API_S3[0],
+            aws_secret_access_key=TOKEN_API_S3[1]
+        )
+        s3.upload_file(source_file_name, bucket_name, cloud_file_name)
+        duration = "{:.1f}".format(time.time() - time_start_temp) + ' seconds'
+        res = f'SUCCESS ({duration}): {bucket_name}/{cloud_file_name}'
+    except Exception as e:
+        res = f'FAILURE: {source_file_name}\n\n{e}'
+    
+    return res
+
+
+# get latest view of bucket (S3)
+def read_s3(BUCKET=None):
+    BASE_URL = f'https://{BUCKET}.s3.ap-southeast-1.amazonaws.com/'
+
+    df = pd.read_xml(BASE_URL)
+    df = df.dropna(subset=['Key'])[['Key','LastModified']]
+    df.columns = ['key','modified']
+    df.modified = pd.to_datetime(df.modified).astype(str).str[:19]
+    df.modified = pd.to_datetime(df.modified) + timedelta(hours=8)
+    df['URL'] = BASE_URL + df.key
+    df = df.sort_values(by='modified',ascending=False).reset_index(drop=True)
+
+    return df
+
+
+# write csv and parquet simultaneously
+def write_csv_parquet(FILEPATH, df=None):
+    df.to_csv(f'{FILEPATH}.csv', index=False)
+    df.to_parquet(f'{FILEPATH}.parquet', index=False, compression='brotli')
+    print(f'Wrote CSV + Parquet: {FILEPATH}')
+
+
+# write parquet with customisation
+def write_parquet(FILEPATH, df=None):
+    df.to_parquet(f'{FILEPATH}.parquet', index=False, compression='brotli')
+    print(f'Wrote Parquet: {FILEPATH}')
+  
+
+# write CSV with customisation
[…]

### 2025-05-02 tex/manuscript.tex
Fix: Party master, Mukhriz entries

@@
 			\LARGE
-			The Malaysian Election Corpus: Federal and State Election Results from 1955 to the Present\\[0.21in]
+			The Malaysian Election Corpus: Federal and State Election Results from 1955 to 2025 \\[0.21in]
 			\Large
@@
 Sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex\cite{ge00report} ea commodo consequat.
+Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex\cite{ge00report,ge01report,ge02report,ge03report,ge04report,ge05report,ge06report,ge07report,ge08report,ge09report,ge10report,ge11report} ea commodo consequat.
 

### 2025-05-02 compile.py
Fix: Names and areas

@@ -32,22 +32,22 @@ def compile_ballots():
             tf = tf[['date','election'] + COL_ORI]
             
             # Generate total valid votes for each seat, and then derive percentage of votes for each candidate
-            sf = tf[['seat','votes']].groupby('seat').sum().reset_index().rename(columns={'votes':'votes_perc'})
-            tf = pd.merge(tf,sf,on='seat',how='left')
+            sf = tf[['date','seat','votes']].groupby(['date','seat']).sum().reset_index().rename(columns={'votes':'votes_perc'})
+            tf = pd.merge(tf,sf,on=['date','seat'],how='left')
             tf.votes_perc = tf.votes/tf.votes_perc * 100
 
             # Classify results
             tf['result'] = 'lost'
             tf.loc[tf.votes_perc < 12.5, 'result'] = 'lost_deposit'
             tf['nameseat'] = tf.name + tf.seat
-            sf = tf[['nameseat','seat','votes']].sort_values(by=['seat','votes']).drop_duplicates(subset='seat',keep='last')
+            sf = tf[['date','nameseat','seat','votes']].sort_values(by=['seat','votes']).drop_duplicates(subset=['date','seat'],keep='last')
             tf.loc[tf.nameseat.isin(sf.nameseat.tolist()), 'result'] = 'won'
             tf = tf.drop('nameseat',axis=1)
             tf.loc[(tf.votes == 0) & (tf.votes_perc != 0), 'result'] = 'won_uncontested'
 
             df = tf.copy() if len(df) == 0 else pd.concat([df,tf],axis=0,ignore_index=True)
 
-    assert len(df.drop_duplicates(subset=['election','state','seat'])) == len(df[df.result.str.contains('won')]), 'Number of winners and contests does not match!'
+    assert len(df.drop_duplicates(subset=['date','election','state','seat'])) == len(df[df.result.str.contains('won')]), 'Number of winners and contests does not match!'
     write_csv_parquet('src-data/consol_ballots',df=df)
     TPYES = {'GE':'federal','SE':'state','BY-ELECTION':'byelection'}
     for k,v in TPYES.items():
@@ -86,9 +86,9 @@ def compile_summary():
     w1 = wf[wf.result.str.contains('won')]
     w2 = wf[~wf.result.str.contains('won')]\
         .sort_values(by=['votes'],ascending=False)\
[…]

### 2025-05-02 dashboards.py

@@ -1,0 +1,281 @@
+import pandas as pd
+import numpy as np
+import json as j
+
+from helper import generate_slug, get_states, write_parquet
+
+PATH = 'src-data/dashboards'
+
+nm = pd.read_csv('src-data/candidates_master.csv').drop_duplicates(subset=['candidate_uid'],keep='last')
+MAP_NAME = dict(zip(nm.candidate_uid,nm.name))
+
+
+# Note: Candidates forms the base for Seat Search and Party Search, as well as Parties / Ballots
+def make_candidates():
+    """Generate candidates dataframe with election results and metadata.
+
+    Reads candidate data from ballot and summary files, maps candidate UIDs to names,
+    adds seat and election metadata, and calculates vote percentages and majorities.
+
+    The function:
+    1. Maps candidate UIDs to standardized names from candidates_master.csv
+    2. Adds seat metadata (type, state) and election details
+    3. Merges with summary statistics (turnout, rejected votes, majorities)
+    4. Writes final dataframe to parquet format
+
+    Returns:
+        Number of rows in the final dataframe, representing the number of candidates across all elections
+    """
+
+    COL_BALLOT = ['slug','name','type','date','election_name','seat','party','votes','votes_perc','result']
+
+    df = pd.read_parquet('src-data/consol_ballots.parquet').rename(columns={'election':'election_name'})
+    df['seat'] = df['seat'] + ', ' + df['state']
+    df = df.drop(['state','area_name'],axis=1)
+    assert len(df[~df.candidate_uid.isin(MAP_NAME.keys())]) == 0, f'Candidate UIDs not found in name map! {df[~df.candidate_uid.isin(MAP_NAME.keys())].candidate_uid.unique()}'
+    df['name'] = df['candidate_uid'].map(MAP_NAME)
+    df['slug'] = df['candidate_uid'].astype(str).str.zfill(5)
+    df.election_name = df.election_name.str.replace('BY-ELECTION','By-Election')
+    df['type'] = 'parlimen'
+    df.loc[df.seat.str.startswith('N.'),'type'] = 'dun'
+    df = df[COL_BALLOT]
+
+    COL_SUMMARY = ['date','election_name','seat','voter_turnout','voter_turnout_perc','votes_rejected','votes_rejected_perc','majority','majority_perc']
+    tf = pd.read_parquet('src-data/consol_summary.parquet')\
[…]

### 2025-05-04 compile.py
Fix: Data entry errors

@@ -124,6 +124,9 @@ def validate():
     df['check'] = df.votes_valid - df.votes_valid_derived
     df['check_perc'] = df.check.abs() / df.votes_valid * 100
     if len(df[df.check != 0]) > 0:
+        df = df.sort_values(by=['date','state','seat']).drop('check_perc',axis=1)
+        df = df[~((df.state == 'Sarawak') & (df.election == 'SE-09'))]
+        df = df[['check'] + list(df.columns[:-1])]
         df[df.check != 0].to_csv('logs/check.csv',index=False)
         raise Exception(f'Validation failed for {len(df[df.check != 0])} seats!')
 

### 2025-05-04 compile.py
Checkpoint: 100% internally validated

@@ -123,9 +123,10 @@ def validate():
     df = pd.merge(df,bf,on=COL_JOIN,how='left')
     df['check'] = df.votes_valid - df.votes_valid_derived
     df['check_perc'] = df.check.abs() / df.votes_valid * 100
+
+    df = df[~((df.state == 'Sarawak') & (df.election == 'SE-09'))] # known issue due to lack of summary data
     if len(df[df.check != 0]) > 0:
         df = df.sort_values(by=['date','state','seat']).drop('check_perc',axis=1)
-        df = df[~((df.state == 'Sarawak') & (df.election == 'SE-09'))]
         df = df[['check'] + list(df.columns[:-1])]
         df[df.check != 0].to_csv('logs/check.csv',index=False)
         raise Exception(f'Validation failed for {len(df[df.check != 0])} seats!')

### 2025-05-04 compile.py
Fix: Lookup naming, non-UTF charS

@@ -4,7 +4,7 @@ import json as j
 
 from helper import get_states, write_csv_parquet
 
-dates = j.load(open('src-data/dates_master.json'))
+DATES = j.load(open('src-data/lookup_dates.json'))
 STATES = get_states(my=1)
 
 
@@ -28,7 +28,7 @@ def compile_ballots():
 
             COL_ORI = [x for x in tf.columns if x not in ['date','election']]
             tf['election'] = f'{NAME}-{e:02d}' if TYPE != 'prk' else NAME
-            if TYPE != 'prk': tf['date'] = dates[s][str(e)] 
+            if TYPE != 'prk': tf['date'] = DATES[s][str(e)] 
             tf = tf[['date','election'] + COL_ORI]
             
             # Generate total valid votes for each seat, and then derive percentage of votes for each candidate
@@ -74,7 +74,7 @@ def compile_summary():
 
             COL_ORI = [x for x in tf.columns if x not in ['date','election']]
             tf['election'] = f'{NAME}-{e:02d}' if TYPE != 'prk' else NAME
-            if TYPE != 'prk': tf['date'] = dates[s][str(e)] 
+            if TYPE != 'prk': tf['date'] = DATES[s][str(e)] 
             tf = tf[['date','election'] + COL_ORI]
 
             df = tf.copy() if len(df) == 0 else pd.concat([df,tf],axis=0,ignore_index=True)

### 2025-05-04 dashboards.py

@@ -6,7 +6,7 @@ from helper import generate_slug, get_states, write_parquet
 
 PATH = 'src-data/dashboards'
 
-nm = pd.read_csv('src-data/candidates_master.csv').drop_duplicates(subset=['candidate_uid'],keep='last')
+nm = pd.read_csv('src-data/lookup_candidates.csv').drop_duplicates(subset=['candidate_uid'],keep='last')
 MAP_NAME = dict(zip(nm.candidate_uid,nm.name))
 
 
@@ -18,7 +18,7 @@ def make_candidates():
     adds seat and election metadata, and calculates vote percentages and majorities.
 
     The function:
-    1. Maps candidate UIDs to standardized names from candidates_master.csv
+    1. Maps candidate UIDs to standardized names from lookup_candidates.csv
     2. Adds seat metadata (type, state) and election details
     3. Merges with summary statistics (turnout, rejected votes, majorities)
     4. Writes final dataframe to parquet format
@@ -147,11 +147,11 @@ def make_parties():
 def make_dates():
     """Generate dates dataframe with election dates and metadata.
 
-    Reads election dates from dates_master.csv, standardizes election names,
+    Reads election dates from lookup_dates.csv, standardizes election names,
     and combines state-level and national-level elections.
 
     The function:
-    1. Reads election dates from dates_master.csv
+    1. Reads election dates from lookup_dates.csv
     2. Standardizes election names to 'SE-XX' format
     3. Combines state-level and national-level elections
     4. Writes final dataframe to parquet format
@@ -159,7 +159,7 @@ def make_dates():
     Returns:
         Number of rows in the final dataframe, representing the number of elections in the dataset
     """
-    df = pd.read_csv('src-data/dates_master.csv').rename(columns={'election_number':'election'})
+    df = pd.read_csv('src-data/lookup_dates.csv').rename(columns={'election_number':'election'})
     df.election = 'SE-' + df.election.astype(str).str.zfill(2)
     df.loc[df.state == 'Malaysia','election'] = df.election.str.replace('SE','GE')
     df = pd.concat([df[df.state == 'Malaysia'],df[df.state != 'Malaysia']],axis=0,ignore_index=True)

### 2025-05-04 dashboards.py
Chore: Tidy env, update dashboards script

@@ -1,9 +1,15 @@
 import pandas as pd
 import numpy as np
 import json as j
+import os
+import time
+from dotenv import load_dotenv
+from requests_toolbelt import MultipartEncoder
+import requests
 
 from helper import generate_slug, get_states, write_parquet
 
+load_dotenv()
 PATH = 'src-data/dashboards'
 
 nm = pd.read_csv('src-data/lookup_candidates.csv').drop_duplicates(subset=['candidate_uid'],keep='last')
@@ -31,7 +37,7 @@ def make_candidates():
 
     df = pd.read_parquet('src-data/consol_ballots.parquet').rename(columns={'election':'election_name'})
     df['seat'] = df['seat'] + ', ' + df['state']
-    df = df.drop(['state','area_name'],axis=1)
+    df = df.drop(['state'],axis=1)
     assert len(df[~df.candidate_uid.isin(MAP_NAME.keys())]) == 0, f'Candidate UIDs not found in name map! {df[~df.candidate_uid.isin(MAP_NAME.keys())].candidate_uid.unique()}'
     df['name'] = df['candidate_uid'].map(MAP_NAME)
     df['slug'] = df['candidate_uid'].astype(str).str.zfill(5)
@@ -45,7 +51,7 @@ def make_candidates():
         .drop(['votes_valid','ballots_not_returned_perc','voters_total'],axis=1)\
         .rename(columns={'ballots_issued':'voter_turnout','voter_turnout':'voter_turnout_perc','election':'election_name'})
     tf['seat'] = tf['seat'] + ', ' + tf['state']
-    tf = tf.drop(['state','area_name'],axis=1)[COL_SUMMARY]
+    tf = tf.drop(['state'],axis=1)[COL_SUMMARY]
     tf.election_name = tf.election_name.str.replace('BY-ELECTION','By-Election')
 
     df = pd.merge(df,tf,on=['date','election_name','seat'],how='right')
@@ -71,14 +77,17 @@ def make_seats():
     """
     COL_WINNER = ['slug','seat_name','seat','state','date','election_name','type','party','name']
 
+    lf = pd.read_csv('src-data/lookup_seats.csv')
+    MAP_AREA_NAME = dict(zip(zip(lf.election, lf.state, lf.seat), lf.area_name))
+
     df = pd.read_parquet(f'src-data/consol_ballots.parquet').rename(columns={'election':'election_name'})
     df['name'] = df['candidate_uid'].map(MAP_NAME)
[…]

### 2025-05-04 dashboards.py
Fix: Filter by-elections out

@@ -123,12 +123,12 @@ def make_parties():
     """
     col_idx = ['party','type','state','election_name','date']
     df = pd.read_parquet(f'{PATH}/elections_candidates.parquet').rename(columns={'seat':'state'})
+    df = df[df.election_name != 'By-Election'] # Remove By-Elections, we are not interested in them
     df = df.drop(['voter_turnout','voter_turnout_perc','votes_rejected','votes_rejected_perc','majority','majority_perc'],axis=1)
     df['state'] = df['state'].apply(lambda x: x.split(',')[1].strip())
     df['seats'] = 0
     df.loc[df.result.str.contains('won'),'seats'] = 1
-    df = df[df.type.isin(['parlimen','dun'])].drop(['name','votes_perc','result','slug'],axis=1)
-    df = df.groupby(col_idx).sum().reset_index()
+    df = df.drop(['name','votes_perc','result','slug'],axis=1).groupby(col_idx).sum().reset_index()
 
     # number of seats and votes per election, by state (sf)
     col_idx_sf = ['election_name','state']
@@ -146,8 +146,6 @@ def make_parties():
 
     df.loc[(df.election_name == 'SE-02') & (df.state == 'Sabah'),'votes_perc'] = df.seats_perc # special case where all seats were uncontested
     df = pd.concat([dfm,df],ignore_index=True)[col_idx + ['seats','seats_total','seats_perc'] + ['votes','votes_perc']]
-    df = df[df.election_name != 'By-Election'] # Remove By-Elections, we are not interested in them
-    write_parquet(f'{PATH}/elections_parties',df=df) 
 
     return len(df)
 

### 2025-05-04 dashboards.py
Fix: Voter totals for Karamunting (SE06) and Hutan Melintang (SE09)

@@ -296,9 +296,9 @@ if __name__ == '__main__':
             'elections_candidates',
             'elections_seats_winner',
             'elections_parties',
-            'elections_dates',
-            'elections_veterans',
-            'elections_slim_big',
+            # 'elections_dates',
+            # 'elections_veterans',
+            # 'elections_slim_big',
         ]:
             time.sleep(10)
             m = MultipartEncoder(

### 2025-05-05 dataviz.py
Feat: Dataviz

@@ -1,0 +1,350 @@
+import pandas as pd
+import json as j
+import matplotlib.pyplot as plt
+import matplotlib.ticker as tkr
+import seaborn as sb
+from helper import get_states
+
+
+# TODO error rate across years
+# TODO validation using 4 vars
+# TODO timeseries of 4 vars
+
+
+def heatmap_seats_federal():
+    dates = j.loads(open('src-data/lookup_dates.json').read())['Malaysia']
+    dates = {int(k):dates[k][:4] for k in dates.keys()}
+
+    df = pd.DataFrame(index=get_states())
+
+    for k in dates.keys():
+        tf = pd.read_csv(f'src-data/federal/ge{k:02d}_summary.csv',usecols=['state'])\
+            .assign(seats=1)\
+            .groupby('state').sum()\
+            .rename(columns={'seats':dates[k]})
+        df = df.join(tf).fillna(0).astype(int)
+    df.columns = [f'{c}\n\n\n\n({df[c].sum()})\n' for c in df.columns]
+    df = df.sort_values(by=df.columns[-1],ascending=False)
+    df.index = df.index + ' '
+    print(f'Total: {df.sum().sum():,} contests at federal level')
+
+    # heatmap
+    fig, ax = plt.subplots(figsize=[11, 7])  # width, height
+    sb.heatmap(df,
+            annot=True, fmt=",.0f",
+            annot_kws={'fontsize': 11},
+            vmin=-1,
+            cmap='Blues',
+            cbar=False,
+            cbar_kws={"shrink": .9}, ax=ax)
+    ax.set_ylabel('')
+    ax.set_xlabel('')
+    ax.set_facecolor('white')
+    # ax.set_title('Seats per Federal Election by State\n', fontsize=10.5, linespacing=1)
+
+    # ticks
+    plt.yticks(rotation=0)
+    ax.tick_params(axis=u'both', which=u'both',
+                length=0, labelsize=11, 
+                labelbottom=False, labeltop=True,
+                bottom=False, top=False)
+    plt.xticks(rotation=0, linespacing=0.3);
+
+    plt.savefig('tex/dataviz/heatmap_seats_federal.png', dpi=400, bbox_inches='tight')
+    plt.savefig('tex/dataviz/heatmap_seats_federal.eps', bbox_inches='tight')
+    plt.close()
+
+
+def heatmap_seats_state():
+    df = pd.read_parquet('src-data/consol_summary.parquet')
[…]

### 2025-05-05 dataviz.py
Fix: Remove TODO

@@ -6,11 +6,6 @@ import seaborn as sb
 from helper import get_states
 
 
-# TODO error rate across years
-# TODO validation using 4 vars
-# TODO timeseries of 4 vars
-
-
 def heatmap_seats_federal():
     dates = j.loads(open('src-data/lookup_dates.json').read())['Malaysia']
     dates = {int(k):dates[k][:4] for k in dates.keys()}

### 2025-05-06 compile.py
Chore: Fix names

@@ -133,6 +133,9 @@ def validate():
 
 
 if __name__ == '__main__':
+    print('\nCompiling ballots:')
     compile_ballots()
+    print('\nCompiling summaries:')
     compile_summary()
+    print('\nValidating:')
     validate()

### 2025-05-06 dashboards.py

@@ -280,6 +280,7 @@ def make_slim_big():
 
 
 if __name__ == '__main__':
+    print('\nGenerating dashboard files:')
     make_candidates()
     make_seats()
     make_parties()
@@ -290,7 +291,7 @@ if __name__ == '__main__':
     TINYBIRD = True
 
     if TINYBIRD:
-        print('\nBeginning Tinybird upload:')
+        print('\nBeginning Tinybird upload:\n')
 
         for FILE in [
             'elections_candidates',
@@ -328,4 +329,4 @@ if __name__ == '__main__':
                 print(r.status_code)
                 print(r.text)
             else:
-                print(f'\n200 OK: {FILE}')
+                print(f'200 OK: {FILE}\n')

### 2025-05-06 dataviz.py

@@ -115,7 +115,7 @@ def heatmap_elections():
             annot=False, fmt=",.0f",
             annot_kws={'fontsize': 11},
             vmin=0,
-            cmap='Blues',
+            cmap='Greys',
             cbar=False,
             linewidths=0.5,
             linecolor=GRID_COLOUR,

### 2025-05-08 fuzzymatch.py
Add fuzzymatching script

@@ -1,0 +1,56 @@
+# intended as a sample of how fuzzymatching was implemented
+
+import pandas as pd
+from rapidfuzz import process, fuzz
+
+
+def get_closest_match(x, choices, scorer=fuzz.token_set_ratio, cutoff=88):
+    match = process.extractOne(x, choices, scorer=scorer, score_cutoff=cutoff)
+    return match[0] if match else None
+
+
+def fuzzy_merge(df1, df2, left_on, right_on, how='inner', scorer=fuzz.token_set_ratio, cutoff=88):
+    df_other = df2.copy()
+    df_other[left_on] = [get_closest_match(x, df1[left_on].tolist(), scorer, cutoff)
+                         for x in df_other[right_on]]
+    return df1.merge(df_other, on=left_on, how=how)
+
+
+def update_candidates(WRITE=False,BALLOTS=None):
+    """
+    Update the candidate master with new candidates from the selected ballots file.
+    Conducts fuzzy matching to avoid generating new UIDs where possible.
+    """
+
+    MASTER = 'src-data/candidates_master.csv'
+
+    res = pd.read_csv(MASTER)
+    res_u = res.copy()
+
+    df = pd.read_csv(BALLOTS,usecols=['name'])
+    df['id'] = df.index + res['id'].iloc[-1] + 1
+    print(f'{len(df)} names to match')
+
+    tf = fuzzy_merge(res_u, df, left_on='name', right_on='name', how='left')
+    tf['id_y'] = tf['id_y'].fillna(-1).astype(int)
+    tf = tf[tf.id_y > -1]
+    print(f'{len(tf)} out of {len(df)} ({len(tf)/len(df):.2%}) names matched')
+    UPDATE_ID = dict(zip(tf.id_y,tf.id_x))
+    df.loc[df.id.isin(tf.id_y.tolist()), 'id'] = df.id.map(UPDATE_ID)
+    UPDATE_UID = dict(zip(df['name'],df['id']))
+
+    res = pd.concat([res,df],axis=0,ignore_index=True)
+    res['len'] = res.name.str.len()
+    res = res.sort_values(by=['id','len']).drop('len',axis=1).drop_duplicates(subset=['name','id']).reset_index(drop=True)
+    if WRITE: 
+        res.to_csv(MASTER,index=False)
+
+    bf = pd.read_csv(BALLOTS)
[…]

### 2025-05-08 tex/manuscript.tex
Submitted manuscript

--- 2025-05-01 tex/manuscript.tex
@@
 \pagenumbering{gobble}
+\def\acronymend{MECo}
+\def\acronym{\acronymend\space}
 
@@
 			\LARGE
-			The Malaysian Election Corpus: Federal and State Election Results from 1955 to the Present\\[0.21in]
+			The Malaysian Election Corpus (\acronymend):\\Federal and State-Level Election Results\\from 1955 to 2025 \\[0.21in]
 			\Large
@@
 		\large 
-		Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+		Empirical research and public knowledge on Malaysia's elections have long been constrained by a lack of high-quality open data, particularly in the absence of a Freedom of Information framework.
+We introduce the Malaysian Election Corpus (MECo; \href{https://electiondata.my}{ElectionData.MY}), an open-access panel database covering all federal and state general elections from 1955 to the present, as well as by-elections from 2008 onward.
+MECo includes candidate- and constituency-level results for nearly 10,000 contests across seven decades, standardised with unique identifiers for candidates, parties, and constituencies.
+The database also provides summary statistics on electorate size, voter turnout, rejected votes, and unreturned ballots.
+This is the most well-curated publicly available data on Malaysian elections, and will unlock new opportunities for research, data journalism, and civic engagement.
 	\end{minipage}
@@
 
+\def\TOTALBALLOTS{25,552}
+\def\TOTALCONTESTS{9,705}
+\def\TOTALPARTIES{99}
+\def\TOTALCONTESTSSTATE{6,935}
+\def\TOTALCONTESTSFEDERAL{2,770}
+\def\TOTALELECTIONS{16}
+
 \section*{Background \& Summary}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex\cite{ge00report} ea commodo consequat.
+Malaysia's electoral history is among the most dynamic in Southeast Asia, encompassing \TOTALCONTESTSFEDERAL\space federal general elections and \TOTALCONTESTSSTATE\space state general elections (Figure \ref{fig:elections}), as well as hundreds of off-cycle by-elections across a multiethnic, multi-party system.
+Furthermore, Malaysia offers significant scope for the study of democratisation, having experienced its first change of ruling party in 2018, and its first ever hung Parliament as recently as 2022.
+However, conducting empirical studies of Malaysian elections is challenging due to the lack of a comprehensive, standardised, and publicly available dataset that provides a single source of truth for scholars.
+The Election Commission (EC) does not publish machine-readable open data which abides by best practices for data sharing, preferring instead to limit citizens to searching up isolated results\cite{mysprsemak}.
+Slightly richer information is available via gazetted election results published as subsidiary legislation\cite{lompub}, but these are published in PDF format only.
+The lack of a Freedom of Information Act further complicates efforts to acquire electoral returns.
+
+\begin{figure}[htbp]
+	\makebox[\textwidth][c]{
+		\begin{minipage}{1.15\textwidth}
+			\centering
+			\caption{Federal and state general election years}
+			\vspace{0.14in}
+			\includegraphics[width=\linewidth]{dataviz/heatmap_elections.eps}
+			\label{fig:elections}
+		\end{minipage}
+	}
+\end{figure}
+
+Amidst this paucity of data, global initiatives such as the Constituency-Level Elections Archive (CLEA)\cite{clea} provide immensely valuable cross-country coverage, including for Malaysian elections.
+However, they generally focus on federal contests, and within that scope, only on the number of votes won by each candidate (thus omitting information such as the electorate size, voter turnout,unreturned ballots, rejected votes, etc).
+Similarly, international turnout or election integrity datasets\cite{icoma2023urnout,norris2014integrity} capture only high-level national indicators.
+Locally, a number of news and civil society organisations\cite{undiinfo,ge15sinar,tindakgithub} compile election data to varying degrees of completeness and quality, but these efforts -- while laudable for their public service, and valuable as a stopgap measure -- typically lack proper data hygiene and standardisation, and are not subjected to systematic validation and review, thus limiting their usefulness for rigorous empirical research and long-term preservation.
+
+In this paper, we address this gap by providing the first comprehensive open database of Malaysian election results at the federal and state level -- we intend for this to be a living resource which provides the go-to empirical foundation for research and journalism on Malaysian elections.
+The database covers \textit{all} general elections since the pre-independence general election in 1955, and 115 by-elections held since 2008.
+In total, it records \TOTALBALLOTS\space ballots cast by \TOTALPARTIES\space individuals representing \TOTALPARTIES\space political parties in \TOTALCONTESTS\space unique electoral contests from 1955 to 2025.
+The dataset comprises two main components:
+\begin{enumbul}
+\item \textbf{Ballots}: The final results for each state legislative assembly constituency (DUN) and federal Parliament constituency (Parliament), with the number of votes received by each candidate.
+\item \textbf{Summaries}: The electorate size, ballots issued, unreturned ballots, and votes rejected in each constituency.
+For each constituency, we also derive the margin of victory (majority), voter turnout rate, vote rejection rate, unreturned ballot rate, and majority as a share of valid votes.
+\end{enumbul}
+
+Furthermore, our database offers three key advantages built on the use of unique identifiers (UIDs).
+First, we encode a UID for each candidate, thus allowing the tracking of a single individual across time, even if they run under different political parties or change the name which they use in public life; this is especially important in Malaysia, because politicians are not required to use their official name on electoral ballots.
+Second, we encode a UID for each party, allowing for tracking of party evolution, such as the expansion of the Alliance Party (\textit{Parti Perikatan}) into the National Front (\textit{Barisan Nasional}).
+Third, we provide a lookup for each unique date-state-constituency combination, allowing for the creation of geospatial lineage and tracking of changes in constituency names.
+In general, the use of UIDs makes our database highly extensible -- a deliberate choice to help other scholars seamlessly build on our work by creating new lookups, rather than altering core datasets.
+
+To the best of our knowledge, no comparable database exists.
+As a living resource, this paper lays the foundation for future data curation, as well as research into areas like malapportionment, gerrymandering, local-level voting patterns, and the spatial dynamics of political competition.
+We also hope that \acronym will serve as a catalyst for broader collaborations between academics, civil society, journalists, and election observers, supporting both scholarly inquiry and public accountability.
+
+Finally, we note that while our work is the first of its kind for Malaysian elections, it follows a growing body of recent academic work focused on compiling and curating country-specific election data for reuse.\cite{perez2021spanish,baltz2022american,de2023american,calderon2025electoral,heddesheimer2025gerda,jensenius2017studying} By situating \acronym within this emerging tradition of high-quality electoral data curation, we contribute to the rapidly-improving global infrastructure of comparative political research.
+This work reflects a commitment to transparency, reproducibility, and the democratisation of access to electoral information.
 
 \section*{Methods}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+There are three sources of data we used to construct our database:
+\begin{enumar}
+\item Physical post-election reports\cite{ge00report,ge01report,ge02report,ge03report,ge04report,ge05report,ge06report,ge07report,ge08report,ge09report,ge10report,ge11report,ge12report,ge13report,sabah1967report,sabah1971report,sabah1976report,sabah1981report,sabah1985report,sabah1986report,sabah1990report,sabah1994report,sabah1999report,sarawak1979report,sarawak1983report,sarawak1987report,sarawak1991report,sarawak1996report,sarawak2001report,sarawak2006report,kelantan1978report}.
+\item Gazetted election results published as subsidiary legislation\cite{lompub}.
+\item Digital results published officially by the EC via a dashboard\cite{mysprsemak}.
+\end{enumar}
+To enable checking and validation, we made images of the post-election reports and PDFs of the gazetted election results (sources 1 and 2) available via this \href{https://kongsi.la/tmECWBT}{anonymous Dropbox link}.
+We constructed \acronym beginning with federal general elections, then state general elections, and finally by-elections.
+This is because state legislative assembly constituencies (DUNs) must lie completely within the boundaries of a federal parliamentary constituency (Parliament), so it was sensible to begin with the superset.
+By-elections coming last is an intuitive choice, since a by-election must follow a general election by definition; validation of by-election data is therefore dependent on having complete federal and state-level results.
+
+\subsection*{Federal General Elections}
+
+\begin{figure}[htbp]
+	\makebox[\textwidth][c]{
+		\begin{minipage}{1.2\textwidth}
+			\centering
+			\caption{Federal election coverage (number of seats)}
+			\vspace{0.14in}
+			\includegraphics[width=1\linewidth]{dataviz/heatmap_seats_federal.eps}
+			\label{fig:federal_coverage}
+		\end{minipage}
+	}
+\end{figure}
+
+For the 3 elections after 8th March 2008 (Figure \ref{fig:federal_coverage}), official results are available digitally via the aforementioned dashboard, in a manner that enabled us to directly scrape the results, albeit with the trial and error generally required for frontend web scraping.
+Where unavailable (all 13 elections prior to and including the 2008 federal general election), we manually (i.e.\ by hand) digitised the data from the aforementioned post-election reports and gazetted results.
+We made a deliberate methodological choice to avoid the use of optical character recognition (OCR) and PDF parsing tools after initial experimentation revealed an average error rate of approximately 10\%, primarily due to frequent changes in formatting and layout, even within the same document.
+We considered this to be unacceptably high for a resource intended to serve as a single source of truth, especially since .
+Moreover, the downstream process of error detection and correction proved to be more time-consuming and error-prone than simply transcribing the data by hand, especially given the relatively manageable size of this data (\TOTALBALLOTS\space ballots across \TOTALCONTESTS\space electoral contests).
+
+As a result, all records acquired from physical books or PDFs were transcribed by hand.
+The Technical Validation section further explains why the way in which Malaysia reports election results made it possible for us to do this with near-total confidence in the accuracy of the final product.
+
+Records for seats in Peninsular Malaysia begin in 1955, while records for seats in Sabah and Sarawak begin in 1969.
+Although there was a federal general election in 1964, one year after Sabah and Sarawak (and Singapore) joined then-Malaya to form the Federation of Malaysia in 1963, seats in Sabah and Sarawak were not contested since the transition agreement allowed their respective state legislatures to appoint (and not elect) their representatives to the federal Parliament.\cite{means1991malaysia} There are no records for Singapore, which was not contested in the 1964 general election for the same reason as Sabah and Sarawak, and which exited the Federation prior to the next federal general election in 1969.
+
+\subsection*{State General Elections}
+
+For state-level general elections, we compiled data using the same three primary sources: post-election reports published by the EC, gazetted election results, and digital results where available.
+The same combination of web scraping and manual digitisation used for federal general elections was applied here.
+
+For states in Peninsular Malaysia, records begin in 1959, when general elections for all 13 state legislative assemblies were held concurrently with the federal general election.
+For Sabah and Sarawak, records begin in 1967 and 1969 respectively, the years of the first state general elections held after the formation of the Federation of Malaysia.
+In all, \acronym contains records for 15 elections for all states in Peninsular Malaysia, 14 elections for Sabah, and 12 for Sarawak (Figure \ref{fig:state_coverage}).
+The reason for the discrepancy between the number of observations for Sabah and Sarawak is that there were two instances in Sabah's electoral history where state general elections were held in relatively quick succession.
+The first was in 1986, when Sabah went to the polls just one year after the previous state general election due to increasing civil and political instability\cite{yusoff2001sabah}.
+The second was in 2020, when Sabah held a state general election two years after the watershed election of 2018 due to a collapse of the state government\cite{lee2020collapse}.
+
+\begin{figure}[htbp]
+	\makebox[\textwidth][c]{
+		\begin{minipage}{1.2\textwidth}
+			\centering
+			\caption{State election coverage (number of seats)}
+			\vspace{0.14in}
+			\includegraphics[width=1\linewidth]{dataviz/heatmap_seats_state.eps}
+			\label{fig:state_coverage}
+		\end{minipage}
+	}
+\end{figure}
+
+\subsection*{By-Elections}
+
+The by-elections dataset covers all Parliament and DUN by-elections held since the 12th federal general election in 2008, totaling 115 contests as of end-April 2025 (Figure \ref{fig:by_coverage}).
+Unlike for general elections, we could not locate any systematically compiled post-election reports or gazetted results for older by-elections.
+As a result, we relied solely on digital results made available via the EC's official website, which only covers by-elections since 2008.
+These digital records were scraped and harmonised with the same schema used for general elections.
+
+\begin{figure}[htbp]
+	\centering
+	\caption{Byelection coverage (number of elections)}
+	\vspace{0.14in}
+	\includegraphics[width=0.8\linewidth]{dataviz/timeseries_byelections.eps}
+	\label{fig:by_coverage}
+\end{figure}
+
+We plan to expand the dataset to include an exhaustive record of previous by-elections once we are able to acquire a reliable source, likely via a combination of EC reports and Hansards from Parliament and State Legislative Assemblies.
+However, we made the decision not to delay the dissemination of the primary \acronym datasets any further.
+Given that the most recent three election cycles are already fully covered, the exclusion of older by-elections is likely negligible for almost all prospective users.
+
+\subsection*{Unique Identifier (UID) Generation}
+
+The database incorporates unique identifiers (UIDs) for parties and candidates to enable consistent tracking across elections and to facilitate longitudinal analysis.
+Additionally, constituency harmonisation is handled through a pragmatic approach that avoids imposing subjective judgments about boundary changes.
+
+\textbf{Parties.}
+Party UIDs were generated manually, given that the total number of distinct parties in the dataset is relatively small (approximately 100).
+No historical harmonisation was conducted for parties that evolved or rebranded over time.
+For example, \textit{Parti Perikatan} and \textit{Barisan Nasional} are assigned separate UIDs, even though the latter is widely regarded as the successor to the former.
+This approach maintains full historical fidelity and allows users to apply their own ex-post harmonisation logic.
+
+\textbf{Candidates.}
+Candidate UIDs were generated through a combination of fuzzy matching and manual correction, enabling the tracking of individual candidates across multiple elections even when their names changed in spelling, formatting, or title usage over time.
+This is particularly important in the Malaysian context, where candidates frequently acquire new honorifics, adopt different formatting conventions, or have minor spelling variations across election cycles.
+Two illustrative examples highlight the complexity of this task.
+8-time Parliamentarian \textbf{Rafidah Aziz} appeared on ballots across 8 elections in forms including:
+
+\begin{centering}
+
+Rafidah Aziz\\
+Rafidah Bt. Ab. Aziz\\
+Rafidah Bt. Abdul Aziz\\
+Datuk Seri Rafidah Aziz
+
+\end{centering}
+
+Another 8-time Parliamentarian \textbf{Samy Vellu A/L Sangalimuthu} appeared on ballots across 9 elections with variations such as:
+
+\begin{centering}
+
+S. Samy Vellu\\
+Datuk Seri Samy Vellu\\
+S. Samy Vellu A/L Sangalimuthu\\
+Dato' S. Samy Vellu A/L Sangalimuthu
+
+\end{centering}
+Through careful matching and correction, we assigned a single UID to all instances of a candidate to support longitudinal analysis.
+
+\textbf{Constituencies.}
+We deliberately avoided assigning UIDs to constituencies.
+Instead, we rely on the intrinsic uniqueness of the \texttt{date-state-constituency} combination, which guarantees that each contest is uniquely identifiable within its context (since no two constituencies within the same state can have the same name in the same election).
+A left join on these three fields suffices to generate a lookup table via which additional data can be merged.
+To aid users in harmonising constituencies across elections, we provide a field called \texttt{area\_name}, which standardises name changes and spelling variations across time.
+Examples include:
+\begin{align*}
+\text{Temerluh} &\rightarrow \space \text{Temerloh}\\ 
+\text{Teluk Anson} &\rightarrow \space \text{Teluk Intan}\\
+\text{Bagan Datoh} \rightarrow \space \text{Bagan}&\text{ }\text{Datok} \rightarrow \space \text{Bagan Datuk}
+\end{align*}
+We do not currently implement harmonisation for changes involving boundary adjustments or the creation of new constituencies.
+For example, although the seat of Bayan Baru in Penang was carved out of Balik Pulau, we do not merge or tag these together because Balik Pulau remains an active seat name today, and such harmonisation would require subjective judgment.
+Our aim is to provide a flexible foundation that allows users to apply their own harmonisation strategies according to their specific research needs.
 
 \section*{Data Records}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+The data records supporting this paper are available through multiple platforms to facilitate access, transparency, and long-term preservation:
+
+\begin{enumbul}
+\item \textbf{Harvard Dataverse}\\
+All primary datasets (Table \ref{tab:data_records}) are published and versioned on Harvard Dataverse at \url{https://doi.org/10.7910/DVN/O4CRXK}.
+This serves as the canonical archive for replication and reuse.
+
+\item \textbf{GitHub}\\
+The full source code used to process, compile, and validate the data is publicly available under a CC0 license at \url{https://github.com/Thevesh/paper-malaysian-election-corpus}.
+This repository also contains all files made available on Harvard Dataverse in both CSV and the highly efficient Parquet format, as well as raw source files split by state and election type.
+
+\item \textbf{Companion Website}\\
+The data can be interactively explored via \href{https://electiondata.my}{ElectionData.MY}.
+In addition to making the data accessible to non-technical users, the site is intended to serve as the primary channel for continuous updates and future enhancements to \acronymend.
+\end{enumbul}
+
+\begin{table}[H]
+	\def\arraystretch{1.3}
+	\centering
+	\caption{Description of primary datasets}
+	\label{tab:data_records}
+	\vspace{0.14in}
+	\begin{tabular}{L{0.29\linewidth}L{0.69\linewidth}}
+	\toprule
+	\textbf{Filename} & \textbf{Description} \\
+	\midrule
+	\texttt{consol\_ballots} & Candidate-level results for all federal and state elections \\
+	\texttt{federal\_ballots} & Subset of \texttt{consol\_ballots} for federal general elections \\
+	\texttt{state\_ballots} & Subset of \texttt{consol\_ballots} for state general elections \\
+	\texttt{byeelection\_ballots} & Subset of \texttt{consol\_ballots} for by-elections \\ \hline
+	\texttt{consol\_summary} & Summary statistics for all federal and state elections \\
+	\texttt{federal\_summary} & Subset of \texttt{consol\_summary} for federal general elections \\
+	\texttt{state\_summary} & Subset of \texttt{consol\_summary} for state general elections \\
+	\texttt{byeelection\_summary} & Subset of \texttt{consol\_summary} for by-elections \\
+	\texttt{lookup\_candidates} & Standardised candidate names \\
+	\texttt{lookup\_parties} & Standardised party names and abbreviations \\
+	\texttt{lookup\_dates} & Election dates, by state and election type \\
+	\texttt{lookup\_seats} & Standardised constituency names \\
+	\hline
+	\texttt{logs/corrections} & Log of manual corrections applied to ballot issued counts to ensure consistency as described in the Technical Validation section \\
+	\bottomrule
+	\end{tabular}
+\end{table}
+
+Table \ref{tab:ballots_structure} describes the structure of \texttt{*\_ballots} files, while Table \ref{tab:summary_structure} describes the structure of \texttt{*\_summary} files.
+
+\begin{table}[ht]
+	\def\arraystretch{1.3}
+	\centering
+	\caption{Structure of all \texttt{*\_ballots} files}
+	\label{tab:ballots_structure}
+	\vspace{0.14in}
+	\begin{tabular}{L{0.29\linewidth}L{0.69\linewidth}}
+	\toprule
+	\textbf{Variable} & \textbf{Description} \\
+	\midrule
+	\texttt{date} & Date of the election (YYYY-MM-DD) \\
+	\texttt{election} & Election name (e.g., GE-14, SE-10, BY-ELECTION) \\
+	\texttt{state} & State in which the constituency is located \\
+	\texttt{seat} & Code and full name of the seat (e.g., P.052 Bayan Baru) \\
+	\texttt{ballot\_order} & Order in which the candidate appeared on the ballot \\
+	\texttt{name} & Candidate name as it appeared on the ballot paper \\
+	\texttt{candidate\_uid} & Unique identifier for the candidate \\
+	\texttt{party} & Party name as it appeared on the ballot paper \\
+	\texttt{party\_uid} & Unique identifier for the party \\
+	\texttt{votes} & Number of valid votes received by the candidate \\
+	\texttt{votes\_perc} & Share of valid votes received by the candidate (\%) \\
+	\texttt{result} & Outcome (won, won uncontested, lost, lost deposit) \\
+	\bottomrule
+	\end{tabular}
+\end{table}
+
+\begin{table}[ht]
+	\def\arraystretch{1.3}
+	\centering
+	\caption{Structure of all \texttt{*\_summary} files}
+	\label{tab:summary_structure}
+	\vspace{0.14in}
+	\begin{tabular}{L{0.35\linewidth}L{0.65\linewidth}}
+	\toprule
+	\textbf{Variable} & \textbf{Description} \\
+	\midrule
+	\texttt{date} & Date of the election (YYYY-MM-DD) \\
+	\texttt{election} & Type of election (e.g., GE-14, SE-10, BY-ELECTION) \\
+	\texttt{state} & State in which the constituency is located \\
+	\texttt{seat} & Full name of the seat (e.g., P.049 Tanjong) \\
+	\texttt{voters\_total} & Total number of registered voters \\
+	\texttt{ballots\_issued} & Number of ballots issued \\
+	\texttt{ballots\_not\_returned} & Number of ballots not returned (often postal votes) \\
+	\texttt{votes\_rejected} & Number of rejected (spoiled) votes \\
+	\texttt{votes\_valid} & Number of valid votes \\
+	\texttt{majority} & Margin of victory between the top two candidates \\
+	\texttt{voter\_turnout} & Ballots issued as a share of registered voters (\%) \\
+	\texttt{majority\_perc} & Majority as a share of valid votes (\%) \\
+	\texttt{votes\_rejected\_perc} & Rejected votes as a share of ballots returned (\%) \\
+	\texttt{ballots\_not\_returned\_perc} & Unreturned ballots as a share of ballots issued (\%) \\
+	\bottomrule
+	\end{tabular}
+\end{table}
 
 \section*{Technical Validation}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+There are four components of the database which require validation: Numerical data, candidate names, party names, and constituency names.
 
+For numerical data, the way in which Malaysia reports election results makes a unique form of validation possible. First, we define the following variables:
+\begin{align*}
+	I &= \text{Ballots Issued} \\
+	U &= \text{Unreturned Ballots} \\
+	R &= \text{Votes Rejected} \\
+	V_i &= \text{Valid Votes for Candidate } i
+\end{align*}
+For a given contest involving $N$ candidates, the following relationship must hold:
+\begin{align}
+	\label{eq:validation}
+	I - U - R = \sum_{i=1}^{N} V_i
+\end{align}
+In plain language, the implied number of valid votes must be equal to the sum of votes received by all candidates.
+Because $I$, $U$, $R$, and $V_i$ are (and have been) reported separately in all historical election reports and gazetted results, we can leverage this relationship as an almost-foolproof way to validate the accuracy of our manual data entry process.
+For transparency, we detected and corrected errors for 82 out of \TOTALCONTESTS\space contests, implying an error rate of 0.84\%, which is significantly lower than the 10\% error rate we encountered in our initial OCR experiments.
+Importantly, these errors are detectable and fixable, and come without the additional overhead of correcting errors in text data; our familiarity with local geography, politicians, and culture enabled us to transcribe text data rapidly and accurately.
+
+This validation procedure also revealed 115 contests (excluding the 2006 Sarawak state general election, which did not report $I$, $U$, or $R$) for which the data was digitised accurately based on our source material, but which nevertheless failed to satisfy Equation (\ref{eq:validation}).
+These errors presumably occurred due to mistakes in data entry which were not caught and corrected during the original publication process.
+In order to ensure a clean dataset, we applied a standard correction -- for all 115 contests failing validation, we adjust the number of ballots issued (as documented in \texttt{corrections.csv}) such that Equation (\ref{eq:validation}) holds.
+We choose \texttt{ballots\_issued} as the variable to adjust for two reasons.
+First, until the 1989 amendment of the Elections (Conduct of Elections) Regulations 1981 (implemented at the 1989 federal general election), the number of unreturned ballots was not reported.
+Second, because the number of rejected votes is very small relative to the number of ballots issued, using rejected votes as the adjusted variable would have resulted in a much larger correction in percentage terms -- specifically, the correction would have required a 20\% change to the number of rejected votes on average (with several exceeding 50\%), relative to a 0.6\% change to the number of ballots issued (with only one above 5\%, and none above 20\%).
+
+\begin{figure}[htbp]
+	\centering
+	\caption{Error rate in general election years}
+	\vspace{0.14in}
+	\includegraphics[width=0.7\linewidth]{dataviz/timeseries_error_rate.eps}
+	\label{fig:error_rate}
+\end{figure}
+
+An interesting trend emerges when we plot the error rate arising from these 115 contests (Figure \ref{fig:error_rate}).
+The error rate was 0\% up to 1964, but spiked to nearly 8\% in 1969, when elections were severely disrupted by the Emergency.
+By 1978, error rates stabilised below 2\%, and have been constant at 0\% since 2008.
+We posit that this reflects general improvements in data management technology over the decades; we do not have a clear explanation for why no errors were made up to 1964.
+
+\begin{figure}[ht]
+	\centering
+	\caption{Histogram of derived variables}
+	\vspace{0.14in}
+	\includegraphics[width=0.8\linewidth]{dataviz/histogram_validation.eps}
+	\label{fig:histograms}
+\end{figure}
+
+Wrapping up our checks on numerical values, we note that the validation procedure can fail if two errors exactly offset each other.
+Furthermore, it cannot detect errors in the number of registered voters, which does not enter Equation (\ref{eq:validation}).
+To address these limitations, we plotted histograms of 4 derived variables (Figure \ref{fig:histograms}): voter turnout rate, vote rejection rate, unreturned ballot rate, and majority as a share of valid votes.
+All four variables pass the check of being bounded between 0 and 100\%, and display smooth distributions as would be expected if data entry was accurate.
+All outlier values were double-checked; in particular, we verified that extreme instances of high rejected votes or unreturned ballots were not due to mistakes in data entry.
+For example, the DUN of Pangkor in Perak had two instances where over 30\% of ballots were not returned; this was due to historical inefficiencies in the implementation of postal voting for navy personnel\cite{junid2019battle}.
+
+For non-numerical data, we conducted 3 types of checks.
+For parties, the full list of parties was only 100 long, so we manually checked each against publicly available information.
+For constituency names, we generated a list of unique constituency names (1,437 in total), which we manually checked for errors in spelling or syntax.
+The most challenging component was candidate names.
+The scale of the dataset -- \TOTALBALLOTS\space candidates across \TOTALCONTESTS\space contests -- made full manual validation infeasible.
+While we applied rigorous formatting standards during data entry and conducted targeted manual checks for prolific or high-profile candidates, we acknowledge that minor inconsistencies may persist.
+These challenges are amplified by the fact that candidates often change the spelling of their names across elections, acquire new titles and honorifics over time (e.g., Dato', Tan Sri, Haji, Ustaz, academic degrees), and format their names differently in different years (for example, omitting or reordering titles).
+Such variations make consistent longitudinal tracking inherently complex.
+As with all living datasets of this scale, we anticipate incremental improvements over time as users engage with the data and identify potential refinements.
+
+Finally, to ensure accuracy of the database as a whole, we derive seats and votes by party for all elections in the dataset, and ensure that these match against the record of parties in Parliament and State Legislative Assemblies.
 \section*{Usage Notes}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
+
+The Malaysian Election Corpus (\acronymend) is designed to support a wide range of use cases, ranging from rigorous empirical research to rapid data journalism, and even casual civic technology projects.
+In the academic realm, \acronym -- as the first database of its kind for Malaysia -- serves as a foundational resource for research in electoral studies, political science, and public policy.
+Researchers can employ the data to answer important questions about the evolution of Malaysia's electoral system, employing both cross-sectional and longitudinal analysis.
+
+We anticipate that many users will want to extend or adapt the dataset.
+The standardised schema and use of lookup tables enable seamless enrichment and flexible integration with other datasets.
+Some valuable examples include:
+\begin{enumbul}
+\item \texttt{lookup\_candidates} can be enriched with data on candidates' demographic characteristics, such as age, gender, ethnic group, and education level.
+\item \texttt{lookup\_parties} can be enriched with data on party affiliations, or even component parties of coalitions.
+For instance, by adding a \texttt{coalition} field to the lookup, it is possible to assign different UIDs to two candidates representing the same coalition, such that they can be traced to different component parties.
+\item \texttt{lookup\_seats} can be enriched with a \texttt{lineage} field, which might track the geospatial lineage of a constituency, including changes in boundaries over time.
+However, this will require the user to define how constituency identity is determined.
+\end{enumbul}
+As a practical reference for users, the \texttt{dashboards.py} script illustrates how to merge the core datasets with lookup tables to create panel data suitable for interactive dashboards and advanced analyses.
+
+Finally, while rigorous validation has been applied (see Technical Validation), this remains a living database and is intended as such.
+Minor inaccuracies, particularly in the candidate name field, may persist as discussed above.
+We encourage users to report issues or submit improvements via the GitHub repository, which provides full transparency of changes between releases.
 
 \section*{Code Availability}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
 
-\newpage
+All data processing, validation, and compilation was conducted in Python.
+The full source code is publicly available via \href{https://github.com/Thevesh/paper-malaysian-election-corpus}{GitHub under a CC0 license}.
+Three key scripts which users should find particularly useful are:
+
+\begin{enumbul}
+\item \texttt{compile.py}, which generates and validates all tabular datasets published on Harvard Dataverse, with the exception of the \texttt{lookup*.csv} files, which were manually curated.
+\item \texttt{dataviz.py}, which generates all visualisations used in this paper.
+\item \texttt{dashboards.py}, which generates the source files for the interactive visualisations available at \href{https://electiondata.my}{ElectionData.MY}.
+\end{enumbul}
 
@@
 \raggedright
+\linespread{1.1}
+\small
 \let\oldthebibliography\thebibliography
@@
 \endgroup
+
 \section*{Author Contributions}
@@
 The author declares no competing interests.
-The author is not affiliated with any political party, or any private or non-governmental organization that has a vested interest in the outcome of Malaysian elections.
+The author is not affiliated with any political party, or any organization which actively participates in or aims to influence the outcome of Malaysian elections.
 
@@
 This work did not receive any specific funding.
-We thank Rosmadi Fauzi and Zulkanain Abdul Rahman for their helpful feedback on the dataset and manuscript.
-We also gratefully acknowledge Nimesha Thevananthan for their assistance with data collection, as well as Danesh Prakash Chacko of Tindak Malaysia for providing valuable insights and assisting with filling gaps in the data, particularly for Sabah in 1971.
-Finally, we thank the Election Commission (EC) of Malaysia for granting access to well-maintained physical records of historical election results stored in the library at its headquarters.
+We thank Rosmadi Fauzi and Zulkanain Abdul Rahman for their helpful feedback and suggestions on the dataset and manuscript.
+We also gratefully acknowledge Nimesha Thevananthan for their assistance with data collection, as well as Danesh Prakash Chacko of Tindak Malaysia for providing historical insights and filling data gaps, particularly for the Sabah state election in 1971.
+Finally, we thank the EC for granting access to physical records of historical election results via \textit{Pusat Sumber SPR}.
 

### 2025-05-10 tex/manuscript.tex
Autogenerate arXiv tarball

@@
 The database covers \textit{all} general elections since the pre-independence general election in 1955, and 115 by-elections held since 2008.
-In total, it records \TOTALBALLOTS\space ballots cast by \TOTALPARTIES\space individuals representing \TOTALPARTIES\space political parties in \TOTALCONTESTS\space unique electoral contests from 1955 to 2025.
+In total, it records \TOTALBALLOTS\space candidates representing \TOTALPARTIES\space political parties in \TOTALCONTESTS\space unique electoral contests from 1955 to 2025.
 The dataset comprises two main components:

### 2025-05-10 helper.py

@@ -8,6 +8,77 @@ import time
 TOKEN_API_S3 = ('YOUR_ACCESS_KEY', 'YOUR_SECRET_KEY')
 
 
+# generate tarball for arxiv submission
+def make_arxiv_tarball(FILEPATH=None,DATAVIZ_PATH='dataviz/'):
+    import os
+    import tarfile
+    import shutil
+    from pathlib import Path
+
+    if not FILEPATH:
+        return "No FILEPATH provided"
+
+    # Create temporary directory for modified files
+    temp_dir = os.path.join(FILEPATH, 'temp_archive')
+    os.makedirs(temp_dir, exist_ok=True)
+
+    try:
+        # 1. Copy .tex and .bbl files
+        for root, _, files in os.walk(FILEPATH):
+            for file in files:
+                if file.endswith(('.tex', '.bbl')):
+                    src_path = os.path.join(root, file)
+                    rel_path = os.path.relpath(src_path, FILEPATH)
+                    dst_path = os.path.join(temp_dir, rel_path)
+                    
+                    # Create destination directory if it doesn't exist
+                    os.makedirs(os.path.dirname(dst_path), exist_ok=True)
+                    
+                    # For .tex files, modify content
+                    if file.endswith('.tex'):
+                        with open(src_path, 'r', encoding='utf-8') as f:
+                            content = f.read()
+                        
+                        # Replace DATAVIZ_PATH in \includegraphics lines
+                        modified_lines = []
+                        for line in content.split('\n'):
+                            if '\\includegraphics' in line and DATAVIZ_PATH in line:
+                                line = line.replace(DATAVIZ_PATH, '')
+                            modified_lines.append(line)
+                        
+                        with open(dst_path, 'w', encoding='utf-8') as f:
+                            f.write('\n'.join(modified_lines))
+                    else:
+                        shutil.copy2(src_path, dst_path)
+
+        # 2. Copy only .eps and .pdf files from DATAVIZ_PATH to root of temp_dir
+        dataviz_full_path = os.path.join(FILEPATH, DATAVIZ_PATH)
+        if os.path.exists(dataviz_full_path):
+            for root, _, files in os.walk(dataviz_full_path):
+                for file in files:
+                    if file.endswith(('.eps', '.pdf')):
+                        src_path = os.path.join(root, file)
+                        # Copy directly to temp_dir root, not preserving directory structure
[…]

### 2025-05-10 helper.py
Fix: Typo

@@ -1,6 +1,8 @@
 import pandas as pd
 import re
-
+import os
+import tarfile
+import shutil
 import boto3
 from datetime import date,timedelta, datetime
 import time
@@ -9,18 +11,16 @@ TOKEN_API_S3 = ('YOUR_ACCESS_KEY', 'YOUR_SECRET_KEY')
 
 
 # generate tarball for arxiv submission
-def make_arxiv_tarball(FILEPATH=None,DATAVIZ_PATH='dataviz/'):
-    import os
-    import tarfile
-    import shutil
-    from pathlib import Path
-
+def make_arxiv_tarball(FILEPATH=None, DATAVIZ_PATH='dataviz/',TEMP_PATH='temp_archive'):
     if not FILEPATH:
         return "No FILEPATH provided"
 
     # Create temporary directory for modified files
-    temp_dir = os.path.join(FILEPATH, 'temp_archive')
+    temp_dir = os.path.join(FILEPATH, TEMP_PATH)
     os.makedirs(temp_dir, exist_ok=True)
+
+    # Keep track of arcnames for each file to avoid recomputing
+    file_to_arcname = {}
 
     try:
         # 1. Copy .tex and .bbl files
@@ -50,6 +50,9 @@ def make_arxiv_tarball(FILEPATH=None,DATAVIZ_PATH='dataviz/'):
                             f.write('\n'.join(modified_lines))
                     else:
                         shutil.copy2(src_path, dst_path)
+                    
+                    # Store the arcname for this file (relative to FILEPATH)
+                    file_to_arcname[dst_path] = rel_path
 
         # 2. Copy only .eps and .pdf files from DATAVIZ_PATH to root of temp_dir
         dataviz_full_path = os.path.join(FILEPATH, DATAVIZ_PATH)
@@ -61,14 +64,14 @@ def make_arxiv_tarball(FILEPATH=None,DATAVIZ_PATH='dataviz/'):
                         # Copy directly to temp_dir root, not preserving directory structure
                         dst_path = os.path.join(temp_dir, os.path.basename(file))
                         shutil.copy2(src_path, dst_path)
+                        # Store the arcname for this file (just the basename)
+                        file_to_arcname[dst_path] = os.path.basename(file)
 
         # Create tarball
         tar_path = os.path.join(FILEPATH, 'arxiv.tar.gz')
         with tarfile.open(tar_path, 'w:gz') as tar:
-            for root, _, files in os.walk(temp_dir):
-                for file in files:
[…]

### 2025-06-08 dashboards_s3.py
Autogenerate lineage descriptions

@@ -101,19 +101,21 @@ def make_seats():
 
     map_change = {
         'en': {
-            'rename': 'was renamed to',
-            'split': 'was split into',
-            'merge': 'was merged with',
+            'rename': ' was renamed to ',
+            'split': ' was split into ',
+            'merge': ' was merged with ',
         },
         'ms': {
-            'rename': 'dinamakan semula kepada',
-            'split': 'dibahagikan kepada',
-            'merge': 'digabungkan dengan',
+            'rename': ' dinamakan semula kepada ',
+            'split': ' dibahagikan kepada ',
+            'merge': ' digabungkan dengan ',
         }
     }
-    ef = pd.read_csv('src-data/lookup_lineage_desc.csv',dtype=str)
-    ef['change_en'] = ef['from'] + ' ' + ef['type'].map(map_change['en']) + ' ' + ef['to'] + ' in the ' + ef['date'].str[:4] + ' redelineation'
-    ef['change_ms'] = ef['from'] + ' ' + ef['type'].map(map_change['ms']) + ' ' + ef['to'].str.replace(' and ',' dan ') + ' dalam persempadan semula ' + ef['date'].str[:4]
+    ef = pd.read_csv('src-data/lookup_seats_lineage_desc.csv',dtype=str).dropna(how='any')
+    ef['change_en'] = ef['from'] + ef['type'].map(map_change['en']) + ef['to'] + ' in the ' + ef['date'].str[:4] + ' redelineation'
+    ef['change_ms'] = ef['from'] + ef['type'].map(map_change['ms']) + ef['to'].str.replace(' and ',' dan ') + ' dalam persempadan semula ' + ef['date'].str[:4]
+    for lang in ['en','ms']:
+        ef.loc[ef.type == 'carve_out',f'change_{lang}'] = map_change[lang]['carve_out_prefix'] + ef[f'change_{lang}']
 
     sf = pd.read_parquet('src-data/dashboards/elections_seats_winner.parquet')
     sf.slug = sf.seat.apply(generate_slug)

### 2025-11-22 compile.py
Major release: Parties and coalitions

@@ -1,181 +1,142 @@
-"""Module for compiling and validating election data."""
+"""
+Script to produce consol_ballots and consol_stats, the two key source datasets.
 
-import json as j
+Steps:
+    1. Read raw ballots files.
+    2a. Generate derived data for each candidate
+        - Vote percentage
+        - Rank
+        - Result
+    2b. Generate derived data for each seat:
+        - Valid votes
+        - N candidates
+        - Majority
+    3. Merge derived data for each seat with raw stats file.
+    4. Compute derived statistics:
+        - Voter turnout
+        - Majority percentage
+        - Rejected votes percentage
+        - Ballots-not-returned percentage
+    5. Validate the data against expected states.
+    6. Save consolidated outputs.
+    7. Generate subsets for federal, each state, and by-elections
+
+Checks:
+    - No invalid states in raw ballots file
+    - No invalid states in raw stats file
+    - N unique contests (date-election-state-seat combo) in same in ballots and stats
+    - No impossible values > 100% in percentages
+    - Compliance with V = I - U - R
+    - All UIDs for candidates, parties, and coalitions are present in respective lookup files
+    - All unique contests are present in seat lookup file
+"""
+
 import pandas as pd
 import numpy as np
 
 from helper import get_states, write_csv_parquet
 
-with open("src-data/lookup_dates.json", encoding="utf-8") as f:
-    DATES = j.load(f)
-states = get_states(my=1)
 
+def main():
+    """
+    Compile and validate election data from raw source files.
+    Created as a function to prevent unsafe imports.
+    """
+    states = get_states()
+    col_group = ["date", "election", "state", "seat"]
 
-def compile_ballots():
-    """Compile ballot data from various election sources."""
-    df = pd.DataFrame()
-    raw = pd.read_csv('src-data/raw_ballots.csv')
-    raw.date = pd.to_datetime(raw.date).dt.date.astype(str)
+    print("\n --------- Compiling ballots ----------\n")
 
-    for s in states + ["PRK"]:
-        if "W.P." in s:
-            continue
+    df = pd.read_csv("src-data/raw_ballots.csv")
+    df.date = pd.to_datetime(df.date).dt.date
[…]

### 2025-11-22 helper.py

@@ -6,14 +6,11 @@ import shutil
 import tarfile
 import time
 from concurrent.futures import ThreadPoolExecutor, as_completed
-from datetime import timedelta
 from typing import List
 
 import boto3
-import pandas as pd
 from dotenv import load_dotenv
 
-# Load environment variables
 load_dotenv()
 
 # S3 configuration
@@ -27,16 +24,14 @@ s3_client = boto3.client(
 TOKEN_API_S3 = (os.getenv("S3_KEY"), os.getenv("S3_SECRET"))
 
 
-def make_arxiv_tarball(
-    filepath=None, dataviz_path="dataviz/", temp_path="temp_archive"
-):
+def make_arxiv_tarball(filepath=None, dataviz_path="dataviz/", temp_path="temp_archive"):
     """Generate a tarball for arXiv submission.
-    
+
     Args:
         filepath (str): Base path for the files
         dataviz_path (str): Path to data visualization files
         temp_path (str): Path for temporary files
-        
+
     Returns:
         str: Path to the generated tarball
     """
@@ -112,12 +107,12 @@ def make_arxiv_tarball(
 
 def upload_s3(bucket_name=None, source_file_name=None, cloud_file_name=None):
     """Upload a file to S3 bucket.
-    
+
     Args:
         bucket_name (str): Name of the S3 bucket
         source_file_name (str): Path to the source file
         cloud_file_name (str): Name to use in the cloud
-        
+
     Returns:
         str: Status message indicating success or failure
     """
@@ -139,12 +134,12 @@ def upload_s3(bucket_name=None, source_file_name=None, cloud_file_name=None):
 
 def upload_s3_single(bucket_name, source_file_name, cloud_file_name):
     """Upload a single file to S3.
-    
+
     Args:
         bucket_name (str): Name of the S3 bucket
         source_file_name (str): Path to the source file
         cloud_file_name (str): Name to use in the cloud
-        
+
     Returns:
         tuple: (source_file_name, success, message)
     """
@@ -166,12 +161,12 @@ def upload_s3_single(bucket_name, source_file_name, cloud_file_name):
 
 def upload_s3_bulk(bucket_name, files_to_upload, max_workers=50):
     """Upload multiple files to S3 in parallel.
-    
+
     Args:
         bucket_name (str): S3 bucket name
         files_to_upload (list): List of tuples (source_file_name, cloud_file_name)
[…]

### 2025-11-22 compile.py
Fix: Remove Johor 1988 PRK

@@ -51,6 +51,10 @@ def main():
     df.date = pd.to_datetime(df.date).dt.date
     assert len(df[~df.state.isin(states)]) == 0, "Invalid state in raw ballots file!"
 
+    df = df[
+        ~((pd.to_datetime(df.date).dt.year == 1988) & (df.election.str.startswith("BY-")))
+    ]  # Remove Johor 1988 by-elections
+
     grp = df.groupby(col_group)["votes"]
 
     df = df.assign(
@@ -77,6 +81,10 @@ def main():
     sf = pd.read_csv("src-data/raw_stats.csv")
     sf.date = pd.to_datetime(sf.date).dt.date
     assert len(sf[~sf.state.isin(states)]) == 0, "Invalid state in raw stats file!"
+
+    sf = sf[
+        ~((pd.to_datetime(sf.date).dt.year == 1988) & (sf.election.str.startswith("BY-")))
+    ]  # Remove Johor 1988 by-elections
 
     df = df[
         ["date", "election", "state", "seat", "votes_valid", "majority", "n_candidates"]

### 2025-11-23 compile.py
Fix: Error validation output

@@ -109,7 +109,7 @@ def main():
 
     df["check"] = df.ballots_issued - df.ballots_not_returned - df.votes_rejected - df.votes_valid
     if len(df[df.check != 0]) > 0:
-        df = df.sort_values(by=["date", "state", "seat"]).drop("check_perc", axis=1)
+        df = df.sort_values(by=["date", "state", "seat"])
         df = df[["check"] + list(df.columns[:-1])]
         df[df.check != 0].to_csv("logs/check.csv", index=False)
         raise ValueError(f"Validation failed for {len(df[df.check != 0])} seats!")

### 2025-11-23 tex/manuscript.tex
Fix: Typo
Fix: Numerous typos, GE-01 seat ordering
Original manuscript

@@
 \bibliographystyle{unsrt}
+\usepackage{filecontents}
 
@@
 We made a deliberate methodological choice to avoid the use of optical character recognition (OCR) and PDF parsing tools after initial experimentation revealed an average error rate of approximately 10\%, primarily due to frequent changes in formatting and layout, even within the same document.
-We considered this to be unacceptably high for a resource intended to serve as a single source of truth, especially since .
+We considered this to be unacceptably high for a resource intended to serve as a single source of truth.
 Moreover, the downstream process of error detection and correction proved to be more time-consuming and error-prone than simply transcribing the data by hand, especially given the relatively manageable size of this data (\TOTALBALLOTS\space ballots across \TOTALCONTESTS\space electoral contests).
@@
 \begin{align*}
-\text{Temerluh} &\rightarrow \space \text{Temerloh}\\ 
-\text{Teluk Anson} &\rightarrow \space \text{Teluk Intan}\\
-\text{Bagan Datoh} \rightarrow \space \text{Bagan}&\text{ }\text{Datok} \rightarrow \space \text{Bagan Datuk}
+	\text{Temerluh}                                    & \rightarrow \space \text{Temerloh}                         \\
+	\text{Telok Anson}                                 & \rightarrow \space \text{Teluk Intan}                      \\
+	\text{Bagan Datoh} \rightarrow \space \text{Bagan} & \text{ }\text{Datok} \rightarrow \space \text{Bagan Datuk}
 \end{align*}
@@
 \begin{align*}
-	I &= \text{Ballots Issued} \\
-	U &= \text{Unreturned Ballots} \\
-	R &= \text{Votes Rejected} \\
-	V_i &= \text{Valid Votes for Candidate } i
+	I   & = \text{Ballots Issued}               \\
+	U   & = \text{Unreturned Ballots}           \\
+	R   & = \text{Votes Rejected}               \\
+	V_i & = \text{Valid Votes for Candidate } i
 \end{align*}
@@
 
+\begin{filecontents*}{mybib.bib}
+
+	@misc{mysprsemak,
+		title        = {{MySPR Semak}} ,
+		author       = {Election Commission},
+		year         = {2025},
+		url          = {https://mysprsemak.spr.gov.my/semakan/keputusan/pru},
+		note         = {Accessed: 2025-05-05}
+	}
+
+	@misc{lompub,
+		title        = {{Federal Legislation: P.U.(B)}},
+		author       = {Attorney General's Chambers of Malaysia},
+		year         = {2025},
+		url          = {https://lom.agc.gov.my/subsid.php?type=pub},
+		note         = {Accessed: 2025-05-05}
+	}
+
+	@misc{clea,
+		title        = {Constituency-Level Elections Archive},
+		author       = {Kollman, Ken and Hicken, Allen and Caramani, Daniele and Backer, David and Lublin, David},
+		year         = {2024},
+		url          = {http://www.electiondataarchive.org},
+		note         = {Accessed: 2025-05-05}
+	}
+
+	@article{icoma2023urnout,
+		title={The Global Dataset on Turnout {(GD-Turnout)}},
+		author={i Coma, Ferran Mart{\'\i}nez and Van De Maele, Diego Leiva},
+		journal={Electoral Studies},
+		volume={86},
+		pages={102681},
+		year={2023},
+		publisher={Elsevier}
+	}
+
+	@article{norris2014integrity,
+		title={Measuring electoral integrity around the world: A new dataset},
+		author={Norris, Pippa and Frank, Richard W and i Coma, Ferran Mart{\'\i}nez},
+		journal={PS: Political Science \& Politics},
+		volume={47},
+		number={4},
+		pages={789--798},
+		year={2014},
+		publisher={Cambridge University Press}
+	}
+
+	@misc{undiinfo,
+		title        = {undi.info},
+		author       = {MalaysiaKini},
+		year         = {2025},
+		url          = {\url{https://citethis.link/meco1-undi}},
+		note         = {Accessed: 2025-05-05}
+	}
+
+	@misc{ge15sinar,
+		title        = {{GE15 Open Data}},
+		author       = {Sinar Project},
+		year         = {2025},
+		url          = {\url{https://citethis.link/meco1-sinar}},
+		note         = {Accessed: 2025-05-05}
+	}
+
+	@misc{tindakgithub,
+		title        = {Historical Election Results},
+		author       = {{Tindak Malaysia}},
+		year         = {2025},
+		howpublished = {\url{https://citethis.link/meco1-tindak}},
+		note         = {Accessed: 2025-05-05}
+	}
+
+	@article{perez2021spanish,
+		title={Spanish electoral archive. {SEA} database},
+		author={P{\'e}rez, Virgilio and Aybar, Cristina and Pav{\'\i}a, Jose M},
+		journal={Scientific Data},
+		volume={8},
+		number={1},
+		pages={193},
+		year={2021},
+		publisher={Nature Publishing Group UK London}
+	}
+
+	@article{baltz2022american,
+		title={{American} election results at the precinct level},
+		author={Baltz, Samuel and Agadjanian, Alexander and Chin, Declan and Curiel, John and DeLuca, Kevin and Dunham, James and Miranda, Jennifer and Phillips, Connor Halloran and Uhlman, Annabel and Wimpy, Cameron and others},
+		journal={Scientific Data},
+		volume={9},
+		number={1},
+		pages={651},
+		year={2022},
+		publisher={Nature Publishing Group UK London}
+	}
+
+	@article{de2023american,
+		title={{American} local government elections database},
+		author={de Benedictis-Kessner, Justin and Lee, Diana Da In and Velez, Yamil R and Warshaw, Christopher},
+		journal={Scientific Data},
+		volume={10},
+		number={1},
+		pages={912},
+		year={2023},
+		publisher={Nature Publishing Group UK London}
+	}
+
+	@article{heddesheimer2025gerda,
+		title={{GERDA}: The {German} Election Database},
+		author={Heddesheimer, Vincent and Hilbig, Hanno and Sichart, Florian and Wiedemann, Andreas},
+		journal={Scientific Data},
+		volume={12},
+		number={1},
+		pages={618},
+		year={2025},
+		publisher={Nature Publishing Group UK London}
+	}
+
+	@article{calderon2025electoral,
+	title={Electoral precinct-level database for {Mexican} municipal elections},
+	author={Calder{\'o}n-Hern{\'a}ndez, Bruno and Larreguy, Horacio and Marshall, John and P{\'e}rez-Castellanos, Jos{\'e} Luis},
+	journal={Scientific Data},
+	volume={12},
+	number={1},
+	pages={582},
+	year={2025},
+	publisher={Nature Publishing Group UK London}
+	}
+
+	@article{jensenius2017studying,
+	title={Studying {Indian} politics with large-scale data: {Indian} election data 1961--today},
+	author={Jensenius, Francesca R and Verniers, Gilles},
+	journal={Studies in Indian Politics},
+	volume={5},
+	number={2},
+	pages={269--275},
+	year={2017},
+	publisher={SAGE Publications Sage India: New Delhi, India}
+	}
+
+	@book{ge00report,
+		title     = {Report on the First Election of Members to the Legislative Council of the Federation of Malaya},
+		author    = {T. E. Smith},
+		year      = {1955},
+		publisher = {Supervisor of Elections},
+	}
+
+	@book{ge01report,
+		title     = {Report on the Parliamentary and State Elections 1959},
+		author    = {Election Commission},
+		year      = {1959},
+		publisher = {Election Commission of the Federation of Malaya},
+	}
+
+	@book{ge02report,
+		title     = {Report on the Parliamentary (Dewan Ra'ayat) and State Legislative Assembly General Elections, 1964 of the States of Malaya},
+		author    = {Election Commission},
+		year      = {1964},
+		publisher = {Election Commission of the Federation of Malaya},
+	}
+	@book{ge03report,
+		title     = {Report on the Parliamentary (Dewan Ra'ayat) and State Legislative Assembly General Elections 1969 of the States of Malaya, Sabah and Sarawak},
+		author    = {Election Commission},
+		year      = {1971},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{ge04report,
+		title     = {Report on the Parliamentary (Dewan Rakyat) and State Legislative Assembly General Elections 1974 of the States of Malaya and Sarawak},
+		author    = {Election Commission},
+		year      = {1974},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{ge05report,
+		title     = {Report on the General Elections to the House of Representatives and the State Legislative Assemblies Other Than the State Legislative Assemblies of Kelantan, Sabah and Sarawak 1978},
+		author    = {Election Commission},
+		year      = {1978},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{ge06report,
+		title     = {Report on the Malaysian General Elections 1982},
+		author    = {Election Commission},
+		year      = {1982},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{ge07report,
+		title     = {Report on the Malaysian General Elections 1986},
+		author    = {Election Commission},
+		year      = {1986},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{ge08report,
+		title     = {Report on the Malaysian General Elections 1990},
+		author    = {Election Commission},
+		year      = {1990},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{ge09report,
+		title     = {Report of the General Election Malaysia 1995},
+		author    = {Election Commission},
+		year      = {1995},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{ge10report,
+		title     = {Report of the General Election Malaysia 1999},
+		author    = {Election Commission},
+		year      = {1999},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{ge11report,
+		title     = {Report of the General Election Malaysia 2004},
+		author    = {Election Commission},
+		year      = {2004},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{ge12report,
+		title     = {Report of the General Election Malaysia 2008},
+		author    = {Election Commission},
+		year      = {2008},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{ge13report,
+		title     = {Report of the General Election Malaysia 2013},
+		author    = {Election Commission},
+		year      = {2013},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{sabah1967report,
+		title     = {Report on the State Legislative Assembly General Election 1967 of the State of Sabah},
+		author    = {Election Commission},
+		year      = {1967},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{sabah1971report,
+		title     = {Report on the State Legislative Assembly General Election 1971 of the State of Sabah},
+		author    = {Election Commission},
+		year      = {1971},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{sabah1976report,
+		title     = {Report on the State Legislative Assembly General Election 1976 of the State of Sabah},
+		author    = {Election Commission},
+		year      = {1976},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{kelantan1978report,
+		title     = {Report on the State Legislative Assembly General Election 1978 of the State of Kelantan},
+		author    = {Election Commission},
+		year      = {1978},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{sarawak1979report,
+		title     = {Report on the State Legislative Assembly General Election 1979 of the State of Sarawak},
+		author    = {Election Commission},
+		year      = {1979},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{sabah1981report,
+		title     = {Report on the State Legislative Assembly General Election 1981 of the State of Sabah},
+		author    = {Election Commission},
+		year      = {1981},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{sarawak1983report,
+		title     = {Report on the State Legislative Assembly General Election 1983 of the State of Sarawak},
+		author    = {Election Commission},
+		year      = {1983},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{sabah1985report,
+		title     = {Report on the State Legislative Assembly General Election 1985 of the State of Sabah},
+		author    = {Election Commission},
+		year      = {1985},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{sabah1986report,
+		title     = {Report on the State Legislative Assembly General Election 1986 of the State of Sabah},
+		author    = {Election Commission},
+		year      = {1986},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{sarawak1987report,
+		title     = {Report on the State Legislative Assembly General Election 1987 of the State of Sarawak},
+		author    = {Election Commission},
+		year      = {1987},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{sabah1990report,
+		title     = {Report on the State Legislative Assembly General Election 1990 of the State of Sabah},
+		author    = {Election Commission},
+		year      = {1990},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{sarawak1991report,
+		title     = {Report on the State Legislative Assembly General Election 1991 of the State of Sarawak},
+		author    = {Election Commission},
+		year      = {1991},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{sabah1994report,
+		title     = {Report on the State Legislative Assembly General Election 1994 of the State of Sabah},
+		author    = {Election Commission},
+		year      = {1994},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{sarawak1996report,
+		title     = {Report on the State Legislative Assembly General Election 1996 of the State of Sarawak},
+		author    = {Election Commission},
+		year      = {1996},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{sabah1999report,
+		title     = {Report on the State Legislative Assembly General Election 1999 of the State of Sabah},
+		author    = {Election Commission},
+		year      = {1999},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{sarawak2001report,
+		title     = {Report on the State Legislative Assembly General Election 2001 of the State of Sarawak},
+		author    = {Election Commission},
+		year      = {2001},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{sarawak2006report,
+		title     = {Report on the State Legislative Assembly General Election 2006 of the State of Sarawak},
+		author    = {Election Commission},
+		year      = {2006},
+		publisher = {Election Commission of Malaysia},
+	}
+
+	@book{means1991malaysia,
+		author    = {Gordon P. Means},
+		title     = {Malaysia: The Second Generation},
+		publisher = {Oxford University Press},
+		address   = {Singapore},
+		year      = {1991}
+	}
+
+	@article{yusoff2001sabah,
+		title={Sabah politics under {Pairin}},
+		author={Yusoff, Mohammad Agus},
+		journal={JATI - Journal of Southeast Asian Studies},
+		volume={6},
+		pages={29--48},
+		year={2001}
+	}
+
+	@article{lee2020collapse,
+		title={The Collapse of the State Government in {Sabah}: Back to the Drawing Board},
+		author={Lee, P.O.},
+		journal={ISEAS - Yusof Ishak Institute Commentaries},
+		year={2020},
+		note={Available at: \url{https://citethis.link/meco1-iseas}}
+	}
+
+	@incollection{junid2019battle,
+		title={The battle for {Perak}},
+		author={Junid, Iskandar Dzulkarnain Ahmad},
+		booktitle={Malaysia's 14th General Election and {UMNO}'s Fall},
+		pages={223--239},
+		year={2019},
+		publisher={Routledge}
+	}
+\end{filecontents*}
+
 % this section generates reference

### 2025-11-23 dataviz.py
Updated dataviz

@@ -1,131 +1,25 @@
-"""Module for generating data visualizations for election results."""
+"""
+Generates all data visualisations used in the paper.
+Dataviz generated:
+    1. Bitmap of election years for federal and state elections
+    2. Heatmap table of Parliamentary seats by state over time
+    3. Heatmap table of DUN seats by state over time
+    4. Timeseries of by-elections since 2008
+    5. Timeseries of error rate since 1964
+    6. Histogram of percentage variables for validation
+    7. Pyramid of candidates by age and sex where both exist
+"""
 
 import json as j
 import pandas as pd
 import matplotlib.pyplot as plt
 import matplotlib.ticker as tkr
+from matplotlib.ticker import FixedLocator, FuncFormatter
 import seaborn as sb
+
 from helper import get_states
 
-# Set style
-plt.style.use("seaborn")
 sb.set_palette("husl")
-
-
-def heatmap_seats_federal():
-    """Plot seat distribution by state over time."""
-    dates = j.loads(open("src-data/lookup_dates.json",
-                         encoding="utf-8").read())["Malaysia"]
-    dates = {int(k): dates[k][:4] for k in dates.keys()}
-
-    df = pd.DataFrame(index=get_states())
-
-    for k in dates.keys():
-        tf = (
-            pd.read_csv(f"src-data/federal/ge{k:02d}_summary.csv", usecols=["state"])
-            .assign(seats=1)
-            .groupby("state")
-            .sum()
-            .rename(columns={"seats": dates[k]})
-        )
-        df = df.join(tf).fillna(0).astype(int)
-    df.columns = [f"{c}\n\n\n\n({df[c].sum()})\n" for c in df.columns]
-    df = df.sort_values(by=df.columns[-1], ascending=False)
-    df.index = df.index + " "
-    print(f"Total: {df.sum().sum():,} contests at federal level")
-
-    # heatmap
-    _, ax = plt.subplots(figsize=[11, 7])  # width, height
-    sb.heatmap(
-        df,
-        annot=True,
-        fmt=",.0f",
-        annot_kws={"fontsize": 11},
-        vmin=-1,
-        cmap="Blues",
-        cbar=False,
-        cbar_kws={"shrink": 0.9},
-        ax=ax,
-    )
-    ax.set_ylabel("")
-    ax.set_xlabel("")
-    ax.set_facecolor("white")
[…]

### 2025-11-28 tex/manuscript-r1.tex
Feat: Manuscript Revision-1

\documentclass[11pt]{article}
\usepackage[toc,page]{appendix}
\RequirePackage{fix-cm}
\usepackage[utf8]{inputenc}
\usepackage[margin=1.5in]{geometry}
\usepackage[bottom, flushmargin]{footmisc}
\setlength{\footnotesep}{\baselineskip} % space between footnotes 
\setlength{\parindent}{0in} % space at start of paragraph
\setlength{\parskip}{0.14in} % space between paragraphs
\linespread{1.25}
\usepackage{titlesec}
\titlespacing\section{0pt}{0.21in}{0.03in}
\titlespacing\subsection{0pt}{0.21in}{0.01in}
\titlespacing\subsubsection{0pt}{0.21in}{0in}
\usepackage{marginnote}
\newcommand{\marnum}[1]{\reversemarginpar \marginnote{#1}[0.14in]}

% bibliography-related packages
\usepackage[superscript]{cite}
\bibliographystyle{unsrt}

% lists
\usepackage{enumitem} 
\newcommand{\bulletlabel}{\raisebox{0.2ex}{\small$\bullet$}}
\newlist{enumbul}{enumerate}{6}
\setlist[enumbul]{label=\bulletlabel, topsep=0pt, leftmargin=0.3in, rightmargin=0.3in}
\newlist{enumar}{enumerate}{6}
\setlist[enumar]{label=\arabic*$)$,topsep=0pt, leftmargin=0.3in, rightmargin=0.3in}

% packages vital for various things
\usepackage{hyperref}
\usepackage{comment} % commenting out a large chunk
\usepackage{enumitem} % lists
\usepackage{graphicx,nicefrac} % graphics, especially external ones
\graphicspath{ {dataviz/} }
\usepackage{amsmath} % writing math
\usepackage{amssymb} % writing symbols
\usepackage{amsthm}
\usepackage{bm}
\usepackage{float}
\usepackage{mathtools}
\usepackage{bigints}

% colors
\usepackage{tcolorbox}
\usepackage{color} % colors
\usepackage{xcolor, colortbl} % more control over colors
\newcommand{\red}[1]{\color{red}#1\color{black}}
\newcommand{\green}[1]{\color{green!80!black}#1\color{black}}
\newcommand{\blue}[1]{\color{blue}#1\color{black}}
\newcommand{\gray}[1]{\color{gray!80!black}#1\color{black}}
\newcommand{\black}[1]{\color{black}#1\color{black}}

\hypersetup{
	colorlinks,
	linkcolor=black, %internal links
	urlcolor=cyan,  % URLs
	citecolor= red, % references
	breaklinks=true
}

% for use in tables
\usepackage{multirow}
\usepackage{multicol}
\usepackage{array}
\usepackage{booktabs}
\newcommand\bstrut{\rule{0pt}{2.5ex}} % space before row
\newcommand\astrut{\rule[-1.25ex]{0pt}{0pt}} % space after row
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

%miscellaneous
\newcommand{\ansm}[1]{\text{\framebox{\ensuremath{#1}}}}
\newcommand{\anst}[1]{\text{\framebox{#1}}}
\newcommand{\ie}[1][]{\textit{i.e.\ }#1}
\newcommand{\eg}[1][]{\textit{e.g.\ }#1}
\newcommand\pspace {\\[0.07in]}
\newcommand\ppspace {\\[0.14in]}
\newcommand{\logsep}{\begin{center}---------------\end{center}}

\def\highlight#1#2{
	\begin{centering}

		\vspace{1.2ex}
		\begin{minipage}{0.8\linewidth}
			\begin{tcolorbox}[boxsep = 3.3pt, boxrule=0.4pt, colback = white, colbacktitle=white, coltitle = black, colframe= black, title=\centering \textbf{#1}]
				\centering
				#2
			\end{tcolorbox}
		\end{minipage}
		\vspace{1.2ex}

	\end{centering}
}

\begin{document}
\pagenumbering{gobble}
\def\acronymend{MECo}
\def\acronym{\acronymend\space}

\def\TOTALBALLOTS{25,545}
\def\TOTALCONTESTS{9,704}
\def\TOTALPARTIES{110}
\def\TOTALCOALITIONS{18}
\def\TOTALCONTESTSSTATE{6,936}
\def\TOTALCONTESTSFEDERAL{2,715}
\def\TOTALCONTESTSBYELEC{53}
\def\TOTALELECTIONS{16}
\def\UNIQUECANDIDATES{14,000}
\def\TOTALCORRECTIONS{115}

\phantom{Thevesh}

\vfill

\begin{center}
	\begin{minipage}{0.88\linewidth}
		\begin{center}
			\LARGE
			The Malaysian Election Corpus (\acronymend):\\Federal and State-Level Election Results\\from 1955 to 2025 \\[0.21in]
			\Large
			Thevesh Thevananthan\\[0.15in]  % ← Author name inserted here
		\end{center}
		\large
		Empirical research and public knowledge on Malaysia's elections have long been constrained by a lack of high-quality open data, particularly in the absence of a Freedom of Information framework. This paper introduces the Malaysian Election Corpus (MECo), an open-access panel database covering all federal and state general elections since 1955, as well as by-elections since 2008. MECo includes candidate- and constituency-level data for 9,704 electoral contests across seven decades, standardised with unique identifiers for candidates, parties, and coalitions. The database also provides summary statistics for each contest (electorate size, voter turnout, majority size, rejected ballots, unreturned ballots), key demographic data for candidates (age, gender, ethnicity), and lineage data for political parties. MECo is the most well-curated open database on Malaysian elections to date, and will unlock new opportunities for research, data journalism, and civic engagement.
	\end{minipage}
\end{center}

\vfill

\phantom{Word Count:}

\newpage
\pagenumbering{arabic}

\section*{Background \& Summary}
Malaysia's electoral history is among the most dynamic in Southeast Asia, encompassing \TOTALCONTESTSFEDERAL\space federal election contests and \TOTALCONTESTSSTATE\space state election contests (Figure \ref{fig:elections}), as well as hundreds of off-cycle by-elections across a multiethnic, multi-party system. Furthermore, Malaysia offers significant scope for the study of democratisation, having experienced its first change of ruling party in 2018, and its first ever hung Parliament as recently as 2022. However, empirical studies of Malaysian elections are hindered by the lack of a comprehensive, standardised, and publicly available dataset that provides a single source of truth for scholars. The Election Commission (EC) does not publish open data which abides by best practices for data sharing, preferring instead to limit citizens to searching up isolated results via \href{https://citethis.link/myspr}{MySPR Semak}. Gazetted election results published as subsidiary legislation by the \href{https://citethis.link/warta}{Attorney General's Chambers (AGC)} contain slightly more detail, but are available in PDF format only. The lack of a Freedom of Information Act further complicates efforts to acquire and systematically compile electoral returns.

\begin{figure*}[htb]
	\centering
	\caption{Federal and state general election years}
	\vspace{0.14in}
	\makebox[\textwidth][c]{
		\includegraphics[width=1.1\linewidth]{dataviz/heatmap_elections.eps}
	}
	\label{fig:elections}
\end{figure*}

Amidst this paucity of data, global initiatives such as the Constituency-Level Elections Archive (CLEA)\cite{clea} provide immensely valuable cross-country coverage, including for Malaysian elections. However, they generally focus on federal contests, and within that scope, only on the number of votes won by each candidate (thus omitting information such as the electorate size, voter turnout, unreturned ballots, rejected ballots, etc). Similarly, international turnout or election integrity datasets\cite{icoma2023turnout,norris2014integrity} capture only high-level national indicators. Locally, a number of news and civil society organisations such as Tindak Malaysia\cite{tindak_data}, malaysiakini (\href{https://citethis.link/undinfo}{undi.info}), and Sinar Project compile election data to varying degrees of completeness and quality, but these efforts -- while laudable for their public service, and valuable as a stopgap measure -- typically lack proper data hygiene and standardisation, and are not subjected to systematic validation and review, thus limiting their usefulness for rigorous empirical research and long-term preservation.

In this paper, I address this gap by providing the Malaysian Election Corpus (MECo),\cite{meco_dataset} the first comprehensive open database of Malaysian election results at the federal and state level. MECo is intended as a living resource which provides the go-to empirical foundation for research and journalism on Malaysian elections. The database covers \textit{all} general elections since the pre-independence general election in 1955, and all \TOTALCONTESTSBYELEC\space by-elections since the 12th federal general election in 2008. In total, it records \UNIQUECANDIDATES\space unique candidates representing \TOTALPARTIES\space political parties in \TOTALCONTESTS\space unique electoral contests from 1955 to 2025.

The dataset comprises two core components:
\begin{enumbul}
	\item \textbf{Ballots}: The final results for each state legislative assembly constituency (DUN) and federal Parliament constituency (Parliament), with the number of votes received by each candidate.
	\item \textbf{Stats}: The electorate size, ballots issued, unreturned ballots, and ballots rejected in each constituency. For each constituency, I also derive the margin of victory (majority), voter turnout rate, ballot rejection rate, unreturned ballot rate, and majority as a share of valid votes.
\end{enumbul}

Furthermore, my database offers three key advantages built on the use of unique identifiers (UIDs). First, I encode a UID for each candidate, allowing a single individual to be tracked across time even when they share a name with other candidates, contest under different parties, or change the name used in public life; this is especially important in Malaysia, where politicians are not required to use their official legal names on electoral ballots. Second, I encode a UID for each party, enabling consistent tracking of political parties even when they undergo rebranding or organisational transformation, such as the evolution of the National Justice Party (PKN) into the People's Justice Party (PKR) in 2003 following a merger with the Malaysian People's Party (PRM). Third, I encode a UID for each coalition, allowing coalition membership to be identified separately from party identity; this is an essential distinction in Malaysia, where election ballots frequently list the coalition rather than the actual party of the candidate. In general, the use of UIDs makes the database highly extensible, allowing other researchers to build new lookup tables or enrich existing ones without needing to alter the core datasets.

To the best of my knowledge, no comparable database exists. As a living resource, this paper lays the foundation for future data curation, as well as research into areas like malapportionment, gerrymandering, local-level voting patterns, and the spatial dynamics of political competition. I also hope that \acronym will serve as a catalyst for broader collaborations between academics, civil society, journalists, and election observers, supporting both scholarly inquiry and public accountability.

Finally, I note that while my work is the first of its kind for Malaysian elections, it follows a growing body of recent academic work focused on compiling and curating country-specific election data for reuse.\cite{perez2021spanish,baltz2022american,de2023american,calderon2025electoral,heddesheimer2025gerda,jensenius2017studying} By situating \acronym within this emerging tradition of high-quality electoral data curation, I contribute to the rapidly-improving global infrastructure of comparative political research. This work reflects a commitment to transparency, reproducibility, and the democratisation of access to electoral information.

\section*{Methods}
There are three main data sources I used to construct my database:
\begin{enumar}
	\item Gazetted election results published in PDF format by the \href{https://citethis.link/lom-pub}{AGC}; searching for ``results of contested election'' or ``keputusan pilihan raya yang dipertandingkan'' will yield the gazetted election results (Form 16, per Regulation 27, Electoral (Conduct of Elections) Regulations 1981). The downloadable PDF contains Malay and English versions of all information.
	\item Physical official election reports\cite{ge00report,ge01report,ge02report,ge03report,ge04report,ge05report,ge06report,ge07report,ge08report,ge09report,ge10report,ge11report,ge12report,ge13report,sabah1967report,sabah1971report,sabah1976report,sabah1981report,sabah1985report,sabah1986report,sabah1990report,sabah1994report,sabah1999report,sarawak1979report,sarawak1983report,sarawak1987report,sarawak1991report,sarawak1996report,sarawak2001report,sarawak2006report,kelantan1978report}.
	\item \href{https://citethis.link/myspr}{MySPR Semak}, an interactive website published by the EC; election results can only be queried one at a time, by selecting the appropriate election type (federal election, state election, or by-election), edition, and constituency. The site is only offered in Malay.
\end{enumar}
It should be noted that the first two sources are legally classified as open data and are not copyrightable under Malaysian copyright law. Section 3(1) of the Copyright Act 1987 (Act 332) expressly excludes from copyright “official texts of the Government or statutory bodies of a legislative or regulatory nature”. The gazetted election results and official election reports fall under this category as formal statutory publications. In the case of the interactive dashboard, the dashboard itself is copyrighted by the EC, but the underlying data is entirely derived from the gazetted results, and is therefore open data. This interpretation was confirmed through consultation with legal advisors and officials familiar with election-document provenance. Accordingly, I archived PDFs of the gazetted election results and post-election reports I used to construct \acronym (see Data Records).

I began with federal general elections, then state general elections, and finally by-elections. This is because state legislative assembly constituencies (DUNs) must lie completely within the boundaries of a federal parliamentary constituency (Parliament), so it was sensible to begin with the superset. By-elections coming last is an intuitive choice, since a by-election must follow a general election by definition; validation of by-election data is therefore dependent on having complete federal and state-level results.

\subsection*{Federal General Elections}

\begin{figure*}[htb]
	\centering
	\caption{Federal election coverage (number of seats)}
	\vspace{0.14in}
	\makebox[\textwidth][c]{
		\includegraphics[width=1.1\textwidth]{dataviz/heatmap_seats_federal.eps}
	}
	\label{fig:federal_coverage}
\end{figure*}

For all federal elections in the dataset (Figure \ref{fig:federal_coverage}), I manually (i.e.\ by hand) digitised or copied the data from the aforementioned sources. I deliberately avoided the use of optical character recognition (OCR), PDF parsing, and web scraping tools after initial experimentation revealed an average error rate of approximately 10\%, primarily due to frequent changes in formatting and layout, even within the same document. I considered this to be unacceptably high for a resource intended to serve as a single source of truth. Moreover, the downstream process of error detection and correction proved to be more time-consuming and error-prone than simply transcribing the data by hand, especially given the relatively manageable size of this data (\TOTALBALLOTS\space rows of data across \TOTALCONTESTS\space electoral contests). The Technical Validation section further explains why the way in which Malaysia reports election results made it possible for me to do this with near-total confidence in the accuracy of the final data released for publication.

Records for seats in Peninsular Malaysia begin in 1955, while records for seats in Sabah and Sarawak begin in 1969. Although there was a federal general election in 1964, one year after Sabah and Sarawak (and Singapore) joined then-Malaya to form the Federation of Malaysia in 1963, seats in Sabah and Sarawak were not contested since the transition agreement allowed their respective state legislatures to appoint (and not elect) their representatives to the federal Parliament.\cite{means1991malaysia} There are no records for Singapore, which was not contested in the 1964 general election for the same reason as Sabah and Sarawak, and which exited the Federation prior to the next federal general election in 1969.

\subsection*{State General Elections}

\begin{figure*}[htb]
	\makebox[\textwidth][c]{
		\begin{minipage}{1.2\textwidth}
			\centering
			\caption{State election coverage (number of seats)}
			\vspace{0.14in}
			\includegraphics[width=1\linewidth]{dataviz/heatmap_seats_state.eps}
			\label{fig:state_coverage}
		\end{minipage}
	}
\end{figure*}

After completing the federal general elections dataset, I constructed the state general elections dataset in exactly the same way.

For states in Peninsular Malaysia, records begin in 1959, when general elections for all 13 state legislative assemblies were held concurrently with the federal general election. For Sabah and Sarawak, records begin in 1967 and 1969 respectively, the years of the first state general elections held after the formation of the Federation of Malaysia. In all, \acronym contains records for 15 elections for all states in Peninsular Malaysia, 14 elections for Sabah, and 12 for Sarawak (Figure \ref{fig:state_coverage}). The reason for the discrepancy between the number of observations for Sabah and Sarawak is that there were two instances in Sabah's electoral history where state general elections were held in relatively quick succession. The first was in 1986, when Sabah went to the polls just one year after the previous state general election due to increasing civil and political instability\cite{yusoff2001sabah}. The second was in 2020, when Sabah held a state general election two years after the watershed election of 2018 due to a collapse of the state government.

\subsection*{By-Elections}

\begin{figure*}[htb]
	\centering
	\caption{By-election coverage (number of elections)}
	\vspace{0.14in}
	\includegraphics[width=0.8\linewidth]{dataviz/timeseries_byelections.eps}
	\label{fig:by_coverage}
\end{figure*}

Unlike for general elections, I could not locate any systematically compiled post-election reports or gazetted results for older by-elections. As a result, I relied solely on digital results made available via the EC's official website, which only covers by-elections since 2008. These digital records were copied, enriched, and standardised with the same schema used for general elections. Consequently, the by-elections dataset covers all Parliament and DUN by-elections held since the 12th federal general election in 2008, totaling 53 contests as of end-April 2025 (Figure \ref{fig:by_coverage}).

I plan to expand the dataset to include an exhaustive record of previous by-elections once I am able to acquire a reliable source, likely via a combination of EC reports and Hansards from Parliament and State Legislative Assemblies. However, given that the most recent three election cycles are already fully covered, the exclusion of older by-elections is likely negligible for almost all prospective users. I therefore made the decision not to delay the dissemination of \acronym any further.

\subsection*{Unique Identifier (UID) and Lookup Table Generation}

The database incorporates unique identifiers (UIDs) for parties, coalitions, and candidates to enable accurate longitudinal analysis. I also provide 3 lookup tables for parties, coalitions, and candidates, which allow users to augment the core datasets, either with variables I have already collated or with their own.

\textbf{Parties and Coalitions.}
Before discussing the generation of party and coalition UIDs, it is critical to distinguish how `party' is defined in this dataset relative to the EC's official records. When a candidate puts their name forth for nomination, they are mandated to declare themselves as either representing an entity registered with the EC, or as an independent candidate. However, the EC's \href{https://citethis.link/spr-parties}{list of registered parties} does not distinguish between a single political party and a coalition of parties. For example, as of 30th October 2025, the list contains - without distinction - both the United Malays National Organisation (UMNO) as well as the Barisan Nasional (BN). The former is a `party' in the conventional sense, while the latter is actually a coalition of several parties, including UMNO itself.

It is debatable as to whether the EC should amend their operating protocols to capture this distinction, or lower the barriers to a party being officially registered and greenlit for listing on a ballot. That judgment notwithstanding, the current set of practices has 3 particularly deleterious consequences for the quality of official election data:

\begin{enumar}
	\item \textbf{Misleading reporting of results for a single election}. Because the choice of party listed on the ballot is made at the candidate level, it is possible for candidates from the same party to list themselves differently. In practice, this happens because parties with a strong local identity choose to contest under the party flag within a particular state, but under the coalition flag in others. For example, the EC's official announcement of the 2022 general election results listed PN and PAS as having won 52 and 22 seats respectively. In actuality, PAS was a component party of PN, but chose to contest in Kelantan and Terengganu under the party flag due to its deep roots in those states. This greatly increases the likelihood of erroneous conclusions by users of official data, especially if they lack the required contextual knowledge.
	\item \textbf{Loss of insight into party dynamics}. Political parties which are part of stable coalitions often choose to contest under the coalitional identity. For example, UMNO - Malaysia's oldest political party - has never contested an election under its own banner, instead contesting under the Alliance flag until 1973, and the BN flag thereafter. This renders it impossible to analyse the political trajectory of UMNO relative to other component parties (especially MIC and MCA) using official data.
	\item \textbf{Loss of insight into unofficial coalitions}. For example, Pakatan Harapan was not officially registered in time for the 2018 general election, thus leading to candidates from its 3 component parties (PKR, DAP, and AMANAH) mostly choosing to contest under the PKR flag. While it is true that contemporaneous election observers were generally fully aware of this circumstance, future researchers may come to a different (incorrect) conclusion if they rely solely on official records.
\end{enumar}

For this reason, I made the methodological choice to capture 3 separate variables (see Data Records for complete schema). First, \texttt{party\_on\_ballot} - which faithfully captures the exact listing of the candidate on the official ballot. Second, \texttt{party} - which captures the true party allegiance of the candidate. Third, \texttt{coalition} - which captures the coalitional allegiance of the party. It was extremely difficult to consolidate this information going back to 1955, especially for state-level results which receive far less attention than federal results - however, I was able to eventually fill in all gaps using a combination of existing scholarly work,\cite{welsh2016elections, hai2017electoral, loh2002democracy, nohlen2001elections} media reports (for modern elections), archived news articles (for older elections), and consultation with colleagues specialising in election history. To the best of my knowledge, MECo is now the only publicly-available dataset with complete data allowing users to distinguish between the 3 dimensions of political allegiance captured here.

Once this was done, party and coalition UIDs were very easy to generate and validate manually, given that the total number of distinct parties (\TOTALPARTIES) and coalitions (\TOTALCOALITIONS) in the dataset is relatively small. The UIDs for coalitions are simple integers, while the UIDs for parties take the following form (e.g. \texttt{001-UMNO}):

\begin{centering}

	\texttt{\{integer\}-\{acronym\}}

\end{centering}

The reason I implemented this syntax is to encode sufficient information for `versioning' within the UID, given that instances of renaming and rebranding are fairly common in Malaysia's political landscape. For example, the Federated Sabah People's Front (UID: \texttt{065-BERSEKUTU}) was founded in 1994, renamed to the Sabah People's Front (\texttt{065-SPF}) in 2010, taken over and rebranded to the Sarawak Workers Party (\texttt{065-SWP}) in 2012, and then renamed again to the present-day Malaysian Nation Party (\texttt{065-PBM}) in 2021. An integer-only approach would have necessitated either `collapsing' these 4 iterations into one UID (resulting in loss of information), or using four different UIDs (resulting in loss of ability to chain versions). My solution enables users to detect that these 4 iterations are part of the same chain (via the 065 prefix), while still maintaining 4 separate rows in a lookup table so that information on each iteration can be provided. This syntax is also handy for distinguishing between parties using the same acronym; for instance, `UPKO' maps to 3 distinct parties which existed at different points in Sabah's election history.

Finally, for political parties, I used the UIDs as the basis for creating a separate lookup table tracking the lineage of political parties, i.e.\ noting down instances of merging, splitting, splintering, and renaming/rebranding linked to the UIDs of the predecessor and successor respectively. I did not deem this necessary for coalitions, which should be analysed by examining their party composition during elections, since coalition membership is always in flux and is independent of changes in the core identity of the coalition.

\textbf{Candidates.}
Candidate UIDs enable the accurate tracking of individual candidates across elections. Beyond the obvious use case of distinguishing candidates with the same name (e.g.\ the dataset contains 8 unique individuals with the exact same name - `Ahmad bin Abdullah'), robust candidate UIDs are particularly important in the Malaysian context, where candidates frequently acquire new honorifics, adopt different formatting conventions, or spell their name differently over time. Two illustrative examples demonstrate the need for candidate UIDs. 8-time Parliamentarian \textbf{Rafidah Aziz} appeared on ballots across 8 elections in forms including:

\begin{centering}

	Rafidah Aziz\\
	Rafidah Bt. Ab. Aziz\\
	Rafidah Bt. Abdul Aziz\\
	Datuk Seri Rafidah Aziz

\end{centering}

Another 8-time Parliamentarian \textbf{Samy Vellu A/L Sangalimuthu} appeared on ballots across 9 elections with variations such as:

\begin{centering}

	S. Samy Vellu\\
	Datuk Seri Samy Vellu\\
	S. Samy Vellu A/L Sangalimuthu\\
	Dato' S. Samy Vellu A/L Sangalimuthu

\end{centering}

Through careful examination, I assigned a single UID to all instances of each candidate, taking particular care to capture all permutations of an individual's name while distinguishing between different individuals who happened to share a name. Two cues were especially useful: \textit{space} and \textit{time}. Consecutive elections in the same seat often revealed consistent candidacy patterns (i.e.\ a `home base'), whereas large gaps across states or decades typically indicated distinct individuals despite identical names. These cues guided targeted searches of external information to ensure that each UID was assigned correctly. Prominent candidates were straightforward to verify, as anyone who won an election appears in public records. The most challenging cases were independent candidates who contested only once, especially in older elections prior to widespread digital documentation. The full process of assigning candidate UIDs took nearly a year; in MECo's present form, I am confident that most, if not all, detectable errors have been eliminated.

Once a complete and validated set of candidate UIDs was established, I created a candidate lookup mapping each UID to a cleaned name stripped of titles and honorifics. This lookup was then enriched with three demographic attributes: sex, ethnicity, and date of birth (DOB). Sex and ethnicity were assigned via manual inspection of names, which are nearly perfectly indicative of sex and strongly indicative of ethnic group in the Malaysian context; both variables are complete for 100\% of candidates. Where possible, these were verified against public records, particularly for recent elections. DOB were obtained through extensive manual searches across thousands of sources - including biographical directories, news archives, parliamentary profiles, and obituary notices - and recorded in ISO format (YYYY-MM-DD). Reliable birth information could not be found for 33.2\% of candidates overall, reflecting limited public documentation in earlier decades. Coverage improves markedly over time: 60\% of candidates in GE3 (1969) lack DOB information, falling to 16\% by GE10 (1999) and under 5\% by GE15 (2022), with remaining gaps concentrated among independent candidates with minimal public profiles.

\subsection*{No UID for Constituencies}

Constituency names are not reliable indicators of spatial continuity. The name of a constituency may remain the same despite substantial spatial change, as in the case of Lumut (Perak) in the 2018 delimitation exercise. Similarly, a constituency may be renamed despite the underlying territory remaining largely intact, as in the case of Silam (Sabah) being renamed to Lahad Datu in the 2019 delimitation exercise. More fundamentally, as several streams of work in the field have illustrated,\cite{hackett2025redrawing,crespin2005using,mcghee2017measuring} the notion of what makes a constituency the same or different across elections is inherently subjective, and should be calibrated to the specific research question at hand. Therefore, any attempt at generating a constituency UID using names alone would be a rough attempt at best, and incredibly misleading at worst.

Consequently, I consider constituency continuity best left to researchers. In fact, it arguably merits dedicated scholarly handling, since electoral lineage has never been rigorously documented or studied in the Malaysian context. That having been said, users who wish to augment \acronym with other constituency-based datasets -- for example, the \href{https://citethis.link/opendosm-parlimen}{subnational statistics} published by the Department of Statistics Malaysia -- should rely on the intrinsic uniqueness of the \texttt{date-state-constituency} combination as a composite key. This avoids imposing any particular lineage model, while ensuring that external data can be merged cleanly and reproducibly.

\section*{Data Records}

All datasets (Table~\ref{tab:data_records}) are published on Harvard Dataverse,\cite{meco_dataset} which serves as the canonical archive. For convenience, the exact same datasets are also mirrored on:

\begin{enumbul}
	\item \textbf{Zenodo}\cite{meco_codebase} (\href{https://doi.org/10.5281/zenodo.17694675}{doi.org/10.5281/zenodo.17694675})\\
	Provides code and raw source files, in addition to datasets.

	\item \textbf{GitHub} (\href{https://github.com/Thevesh/paper-malaysian-election-corpus}{github.com/Thevesh/paper-malaysian-election-corpus})\\
	Facilites active development and maintenance, issue tracking and community contributions. Substantial updates are released on Zenodo.
\end{enumbul}

The datasets fall into two groups; constituency-level statistics and candidate-level ballots, followed by lookup tables that extend the core schema.

\begin{table}[H]
	\centering
	\renewcommand{\arraystretch}{1.05}
	\caption{Description of primary datasets}
	\label{tab:data_records}
	\vspace{0.14in}
	\begin{tabular}{L{0.33\linewidth}L{0.67\linewidth}}
		\toprule
		\textbf{Filename}                  & \textbf{Description}                                                                                           \\
		\midrule
		\texttt{consol\_stats}             & Summary statistics for all federal and state elections                                                         \\
		\texttt{federal\_stats}            & Subset of \texttt{consol\_stats} for federal general elections                                                 \\
		\texttt{state\_***\_stats}         & Subset of \texttt{consol\_stats} for state general elections                                                   \\
		\texttt{byeelection\_stats}        & Subset of \texttt{consol\_stats} for by-elections                                                              \\[0.05in] \hline
		\texttt{consol\_ballots}           & Candidate-level results for all federal and state elections                                                    \\
		\texttt{federal\_ballots}          & Subset of \texttt{consol\_ballots} for federal general elections                                               \\
		\texttt{state\_***\_ballots}       & Subset of \texttt{consol\_ballots} for state general elections                                                 \\
		\texttt{byeelection\_ballots}      & Subset of \texttt{consol\_ballots} for by-elections                                                            \\[0.05in] \hline
		\texttt{lookup\_candidate}         & Standardised list of candidates                                                                                \\
		\texttt{lookup\_party}             & Standardised list of parties                                                                                   \\
		\texttt{lookup\_party\_succession} & Details of merging, splitting, splintering and rebranding                                                      \\
		\texttt{lookup\_coalition}         & Standardised list of coalitions                                                                                \\
		\texttt{lookup\_dates}             & Election dates, by state and election type                                                                     \\[0.05in]
		\hline
		\texttt{logs/corrections}          & Log of manual corrections applied to \texttt{ballots\_issued} as described in the Technical Validation section \\
		\bottomrule
	\end{tabular}
\end{table}

Table~\ref{tab:summary_structure} provides a detailed description of the \texttt{*\_stats} files. Each row corresponds to a single constituency in a single election, and contains the complete set of numerical aggregates for that contest. These files are therefore the best entry point for constituency-level analysis or for merging with external datasets organised at the constituency level. Users should note that the \texttt{*\_stats} files have a one-to-many relationship with the corresponding \texttt{*\_ballots} files; each row in a \texttt{*\_stats} file links to multiple candidate-level rows in the \texttt{*\_ballots} file, except in uncontested seats where only one candidate appears. The two file types can be joined using the composite key \texttt{(date, state, seat)}.

\begin{table}[H]
	\centering
	\renewcommand{\arraystretch}{1.3}
	\caption{Structure of all \texttt{*\_stats} files}
	\label{tab:summary_structure}
	\vspace{0.14in}
	\begin{tabular}{L{0.35\linewidth}L{0.65\linewidth}}
		\toprule
		\textbf{Variable}                     & \textbf{Description}                                 \\
		\midrule
		\texttt{date}                         & Date of the election (YYYY-MM-DD)                    \\
		\texttt{election}                     & Election name (e.g., GE-14, SE-10, BY-ELECTION)      \\
		\texttt{state}                        & State in which the seat is located                   \\
		\texttt{seat}                         & Full name of the seat (e.g., P.049 Tanjong)          \\
		\texttt{voters\_total}                & Total number of registered voters                    \\
		\texttt{ballots\_issued}              & Number of ballots issued                             \\
		\texttt{ballots\_not\_returned}       & Number of ballots not returned (often postal votes)  \\
		\texttt{votes\_rejected}              & Number of rejected (spoiled) ballots                 \\
		\texttt{votes\_valid}                 & Number of valid votes                                \\
		\texttt{majority}                     & Margin of victory (winner minus runner-up)           \\
		\texttt{n\_candidates}                & Number of candidates contesting                      \\
		\texttt{voter\_turnout}               & Ballots issued as a share of registered voters (\%)  \\
		\texttt{majority\_perc}               & Majority as a share of valid votes (\%)              \\
		\texttt{votes\_rejected\_perc}        & Rejected ballots as a share of ballots returned (\%) \\
		\texttt{ballots\_not\_returned\_perc} & Unreturned ballots as a share of ballots issued (\%) \\
		\bottomrule
	\end{tabular}
\end{table}

Table~\ref{tab:ballots_structure} provides a detailed description of the \texttt{*\_ballots} files. Each row corresponds to a single candidate contesting a specific constituency in a specific election. These files are therefore the best entry point for candidate-level analysis or for merging with external datasets organised at the candidate level. Party- or coalition-level analysis should also begin from these files.

\begin{table}[H]
	\centering
	\renewcommand{\arraystretch}{1.3}
	\caption{Structure of all \texttt{*\_ballots} files}
	\label{tab:ballots_structure}
	\vspace{0.14in}
	\begin{tabular}{L{0.29\linewidth}L{0.69\linewidth}}
		\toprule
		\textbf{Variable}          & \textbf{Description}                                    \\
		\midrule
		\texttt{date}              & Date of the election (YYYY-MM-DD)                       \\
		\texttt{election}          & Election name (e.g., GE-14, SE-10, BY-ELECTION)         \\
		\texttt{state}             & State in which the constituency is located              \\
		\texttt{seat}              & Code and full name of the seat (e.g., P.052 Bayan Baru) \\
		\texttt{ballot\_order}     & Order in which the candidate appeared on the ballot     \\
		\texttt{candidate\_uid}    & Unique identifier for the candidate                     \\
		\texttt{name\_on\_ballot}  & Candidate name as it appeared on the ballot paper       \\
		\texttt{party\_on\_ballot} & Party name as it appeared on the ballot paper           \\
		\texttt{party\_uid}        & Unique identifier for the party                         \\
		\texttt{party}             & True party allegiance of the candidate                  \\
		\texttt{coalition\_uid}    & Unique identifier for the coalition                     \\
		\texttt{coalition}         & True coalitional allegiance of the party                \\
		\texttt{votes}             & Number of valid votes received by the candidate         \\
		\texttt{votes\_perc}       & Share of valid votes received by the candidate (\%)     \\
		\texttt{rank}              & Rank of the candidate in that contest                   \\
		\texttt{result}            & Outcome (won, won uncontested, lost, lost deposit)      \\
		\bottomrule
	\end{tabular}
\end{table}

In addition to the primary ballots and statistics files, the database includes 5 lookup tables that support the core datasets. These lookup tables provide a structured way for users to perform deeper analysis or integrate external datasets without needing to modify the core data, thus guarding against downstream errors.

\begin{enumbul}
	\item \texttt{lookup\_candidate}: Standardised list of all candidates, including cleaned names (stripped of titles and honorifics) and demographic attributes (sex, ethnicity, and date of birth). This table should be left-joined onto any \texttt{*\_ballots} file using \texttt{candidate\_uid} as a key.

	\item \texttt{lookup\_party}: Standardised list of political parties, including party acronyms, full party names, and year of formation. This table should be left-joined onto any \texttt{*\_ballots} file using \texttt{party\_uid} as a key.

	\item \texttt{lookup\_party\_succession}: A lineage table documenting instances of parties merging, splitting, splintering, being absorbed, or rebranding. The \texttt{predecessor\_uid} and \texttt{successor\_uid} fields are fully consistent with the \texttt{party\_uid} field in the \texttt{lookup\_party} table, thus enabling joining in either direction as required.

	\item \texttt{lookup\_coalition}: Standardised list of electoral coalitions, including coalition UIDs, names, and short descriptions. This table should be left-joined onto any \texttt{*\_ballots} file using \texttt{coalition\_uid} as a key.

	\item \texttt{lookup\_dates}: A complete listing of all election dates for federal, state, and by-election contests. This table is provided to facilitate preparation of temporal joins with external datasets.
\end{enumbul}

\section*{Technical Validation}
There are five critical components of the database which require validation: Numerical data, candidate names, parties, coalitions, and constituencies.

For numerical data, the way in which Malaysia reports election results makes a unique form of validation possible. First, I define the following variables:
\begin{align*}
	I   & = \text{Ballots Issued}               \\
	U   & = \text{Unreturned Ballots}           \\
	R   & = \text{Ballots Rejected}             \\
	V_i & = \text{Valid Votes for Candidate } i
\end{align*}
For a given contest involving $N$ candidates, the following relationship must hold:
\begin{align}
	\label{eq:validation}
	I - U - R = \sum_{i=1}^{N} V_i
\end{align}
In plain language, the implied number of valid votes must be equal to the sum of votes received by all candidates. Because $I$, $U$, $R$, and $V_i$ are (and have been) reported separately in historical election reports and gazetted results, I can leverage this relationship as an almost-foolproof way to validate the accuracy of my manual data entry process. For transparency, I detected and corrected errors for 82 out of \TOTALCONTESTS\space contests, implying an error rate of 0.84\%, which is significantly lower than the 10\% error rate I encountered in my initial OCR experiments. Importantly, these errors are detectable and fixable, and come without the additional overhead of correcting errors in text data; my familiarity with local geography, politicians, and culture enabled me to transcribe text data rapidly and accurately.

This validation procedure also revealed \TOTALCORRECTIONS\space contests (excluding elections before 1960 which did not report $I$, and the 2006 Sarawak state general election, which did not report $I$, $U$, or $R$) for which the data was digitised accurately based on my source material, but which nevertheless failed to satisfy Equation (\ref{eq:validation}). These errors presumably occurred due to mistakes in data entry which were not caught and corrected during the original publication process. In order to ensure a clean dataset, I applied a standard correction -- for all \TOTALCORRECTIONS\space contests failing validation, I adjusted the number of ballots issued (as documented in \texttt{corrections.csv}) such that Equation (\ref{eq:validation}) holds. I chose \texttt{ballots\_issued} as the variable to adjust for two reasons. First, until the 1989 amendment of the Elections (Conduct of Elections) Regulations 1981 (implemented at the 1989 federal general election), the number of unreturned ballots was not reported (and thus assumed to be 0). Second, because the number of rejected ballots is very small relative to the number of ballots issued, using rejected ballots as the adjusted variable would have resulted in a much larger correction in percentage terms -- specifically, the correction would have required a 20\% change to the number of rejected ballots on average (with several exceeding 50\%), relative to a 0.6\% change to the number of ballots issued (with only one above 5\%, and none above 20\%).

\begin{figure*}[htb]
	\centering
	\caption{Error rate in general election years}
	\vspace{0.14in}
	\includegraphics[width=0.7\linewidth]{dataviz/timeseries_error_rate.eps}
	\label{fig:error_rate}
\end{figure*}

An interesting trend emerges when I plot the error rate arising from these \TOTALCORRECTIONS\space contests (Figure \ref{fig:error_rate}). The error rate was only 0.26\% in 1964 (just 1 error), but spiked to nearly 8\% in 1969, when elections were severely disrupted by the Emergency. By 1978, error rates stabilised below 2\%, and have been constant at 0\% since 2008. I posit that this reflects general improvements in data management technology over the decades; I do not have a clear explanation for the absence of errors in 1964.

\begin{figure*}[htb]
	\centering
	\caption{Histogram of derived variables}
	\vspace{0.14in}
	\includegraphics[width=0.8\linewidth]{dataviz/histogram_validation.eps}
	\label{fig:histograms}
\end{figure*}

Wrapping up my checks on numerical values, I note that the validation procedure can fail if two errors exactly offset each other. Furthermore, it cannot detect errors in the number of registered voters, which does not enter Equation (\ref{eq:validation}). To address these limitations, I plotted histograms of 4 derived variables (Figure \ref{fig:histograms}): voter turnout rate, ballot rejection rate, unreturned ballot rate, and majority as a share of valid votes. All four variables pass the check of being bounded between 0 and 100\%, and display smooth distributions as would be expected if data entry was accurate. All outlier values were double-checked; in particular, I verified that extreme instances of high rejected ballots or unreturned ballots were not due to mistakes in data entry. For example, the DUN of Pangkor in Perak had two instances where over 30\% of ballots were not returned; this was due to historical inefficiencies in the implementation of postal voting for navy personnel\cite{junid2019battle}.

For non-numerical data, I conducted 3 types of checks. For parties and coalitions, the full dataset only contains \TOTALPARTIES\space parties and \TOTALCOALITIONS\space coalitions, so I manually checked each against publicly available information. For constituency names, I generated a list of unique constituency names (1,437 in total), which I manually checked for errors in spelling or syntax. The most challenging component was candidate names and demographic details due to data volume (\TOTALBALLOTS\space rows). Although I applied rigorous formatting standards during data entry and conducted a full round of manual checking (line-by-line), I acknowledge that minor inconsistencies or inaccuracies may persist. This is especially because candidates often change the presentation of their names across elections (e.g., spelling out vs shortening a surname), acquire new titles and honorifics over time (e.g., Dato', Tan Sri, Haji, Ustaz, academic degrees), and format their names differently in different years (e.g., omitting or reordering titles). Such variations make consistent longitudinal tracking inherently complex. As with all living datasets of this scale, I anticipate incremental improvements over time as users engage with the data and identify potential refinements.

Finally, to ensure accuracy of the database as a whole, I derive seats and votes by party for all elections in the dataset, and ensure that these match against the record of parties in Parliament and State Legislative Assemblies.

\section*{Usage Notes}

The Malaysian Election Corpus (\acronymend) is designed to support a wide range of use cases, ranging from rigorous empirical research to rapid data journalism, and even casual civic technology projects. In the academic realm, \acronym -- as the first database of its kind for Malaysia -- serves as a foundational resource for research in electoral studies, political science, and public policy. Researchers can employ the data to answer important questions about the evolution of Malaysia's electoral system, employing both cross-sectional and longitudinal analysis.

The data can also be interactively explored via \href{https://electiondata.my}{ElectionData.MY}. In addition to making the data accessible to non-technical users, the site is intended to serve as the primary channel for continuous updates and enhancements. Future improvements to \acronym will be reflected on the site as new versions (and the corresponding source code) are archived on Harvard Dataverse\cite{meco_dataset} and Zenodo\cite{meco_codebase}, ensuring that users always have easy access to the freshest data.

I anticipate that many users will want to extend or adapt the dataset. The standardised schema and use of lookup tables enable seamless enrichment and integration with other datasets. Some valuable examples include:
\begin{enumbul}
	\item \texttt{lookup\_candidate} can be enriched with additional demographic or biographical information such as marital status, education, and occupation.
	\item \texttt{lookup\_party} and \texttt{lookup\_coalition} can be extended with variables such as ideological classification, membership size, or even beneficial ownership.
	\item Constituency-level data can be merged directly with \acronym using the intrinsic uniqueness of the \texttt{date-state-constituency} combination, thus enabling the use of \acronym in conjunction with official or alternative datasets.
\end{enumbul}
As a practical reference for users, the codebase contains samples (\texttt{dashboards.py}) of how to merge the core datasets with lookup tables to create panel data suitable for interactive dashboards and advanced analyses.

Finally, while rigorous validation has been applied (see Technical Validation), this remains a living database and is intended as such. Minor inaccuracies, particularly in the candidate name field, may persist as discussed above. I encourage users to report issues or submit improvements via the GitHub repository, which provides full transparency of changes between releases.

\section*{Code Availability}

All data processing, validation, and compilation was conducted in Python. The full source code is publicly available under a CC0 license via Zenodo\cite{meco_codebase} and GitHub. Three key scripts which users should find particularly useful are:

\begin{enumbul}
	\item \texttt{compile.py}, which generates and validates all tabular datasets published on Harvard Dataverse, with the exception of the \texttt{lookup*.csv} files, which were manually curated.
	\item \texttt{dataviz.py}, which generates all visualisations used in this paper.
	\item \texttt{dashboards.py}, which generates the source files for the interactive visualisations available at \href{https://electiondata.my}{ElectionData.MY}.
\end{enumbul}

\begin{filecontents*}[overwrite]{mybib.bib}

	@data{meco_dataset,
		author      = {Thevananthan, Thevesh},
		title       = {{The Malaysian Election Corpus}: Federal and State-Level Election Results since 1955},
		year        = {2025},
		publisher   = {Harvard Dataverse},
		doi         = {10.7910/DVN/O4CRXK},
		howpublished= {\url{https://doi.org/10.7910/DVN/O4CRXK}}
	}

	@software{meco_codebase,
		author       = {Thevesh Thevananthan},
		title        = {Thevesh/paper-meco-results},
		year         = 2025,
		publisher    = {Zenodo},
		doi          = {10.5281/zenodo.17694675},
		howpublished = {\url{https://doi.org/10.5281/zenodo.17694675}},
	}

	@data{clea,
		author       = {Kollman, Ken and Hicken, Allen and Caramani, Daniele and Backer, David and Lublin, David},
		title        = {{Constituency-Level Elections Archive (CLEA)}},
		publisher    = {University of Michigan},
		year         = {2024},
		version      = {Ongoing},
		doi          = {10.17616/R33S92},
		howpublished = {\url{https://doi.org/10.17616/R33S92}},
	}

	@article{icoma2023turnout,
		title={The Global Dataset on Turnout {(GD-Turnout)}},
		author={i Coma, Ferran Mart{\'\i}nez and Van De Maele, Diego Leiva},
		journal={Electoral Studies},
		volume={86},
		pages={102681},
		year={2023},
		publisher={Elsevier}
	}

	@article{norris2014integrity,
		title={Measuring electoral integrity around the world: A new dataset},
		author={Norris, Pippa and Frank, Richard W and i Coma, Ferran Mart{\'\i}nez},
		journal={PS: Political Science \& Politics},
		volume={47},
		number={4},
		pages={789--798},
		year={2014},
		publisher={Cambridge University Press}
	}

	@data{tindak_data,
		author       = {Chacko, Danesh Prakash},
		title        = {{Tindak Malaysia Historical Election Results}},
		year         = {2025},
		version      = {archival},
		publisher    = {Zenodo},
		doi          = {10.5281/zenodo.17693558},
		howpublished = {\url{https://doi.org/10.5281/zenodo.17693558}}
	}

	@article{perez2021spanish,
		title={Spanish electoral archive. {SEA} database},
		author={P{\'e}rez, Virgilio and Aybar, Cristina and Pav{\'\i}a, Jose M},
		journal={Scientific Data},
		volume={8},
		number={1},
		pages={193},
		year={2021},
		publisher={Nature Publishing Group UK London}
	}

	@article{baltz2022american,
		title={{American} election results at the precinct level},
		author={Baltz, Samuel and Agadjanian, Alexander and Chin, Declan and Curiel, John and DeLuca, Kevin and Dunham, James and Miranda, Jennifer and Phillips, Connor Halloran and Uhlman, Annabel and Wimpy, Cameron and others},
		journal={Scientific Data},
		volume={9},
		number={1},
		pages={651},
		year={2022},
		publisher={Nature Publishing Group UK London}
	}

	@article{de2023american,
		title={{American} local government elections database},
		author={de Benedictis-Kessner, Justin and Lee, Diana Da In and Velez, Yamil R and Warshaw, Christopher},
		journal={Scientific Data},
		volume={10},
		number={1},
		pages={912},
		year={2023},
		publisher={Nature Publishing Group UK London}
	}

	@article{heddesheimer2025gerda,
		title={{GERDA}: The {German} Election Database},
		author={Heddesheimer, Vincent and Hilbig, Hanno and Sichart, Florian and Wiedemann, Andreas},
		journal={Scientific Data},
		volume={12},
		number={1},
		pages={618},
		year={2025},
		publisher={Nature Publishing Group UK London}
	}

	@article{calderon2025electoral,
	title={Electoral precinct-level database for {Mexican} municipal elections},
	author={Calder{\'o}n-Hern{\'a}ndez, Bruno and Larreguy, Horacio and Marshall, John and P{\'e}rez-Castellanos, Jos{\'e} Luis},
	journal={Scientific Data},
	volume={12},
	number={1},
	pages={582},
	year={2025},
	publisher={Nature Publishing Group UK London}
	}

	@article{jensenius2017studying,
	title={Studying {Indian} politics with large-scale data: {Indian} election data 1961--today},
	author={Jensenius, Francesca R and Verniers, Gilles},
	journal={Studies in Indian Politics},
	volume={5},
	number={2},
	pages={269--275},
	year={2017},
	publisher={SAGE Publications Sage India: New Delhi, India}
	}

	@book{ge00report,
		title     = {Report on the First Election of Members to the Legislative Council of the Federation of Malaya},
		author    = {T. E. Smith},
		year      = {1955},
		publisher = {Supervisor of Elections},
	}

	@book{ge01report,
		title     = {Report on the Parliamentary and State Elections 1959},
		author    = {Election Commission},
		year      = {1959},
		publisher = {Election Commission of the Federation of Malaya},
	}

	@book{ge02report,
		title     = {Report on the Parliamentary (Dewan Ra'ayat) and State Legislative Assembly General Elections, 1964 of the States of Malaya},
		author    = {Election Commission},
		year      = {1964},
		publisher = {Election Commission of the Federation of Malaya},
	}
	@book{ge03report,
		title     = {Report on the Parliamentary (Dewan Ra'ayat) and State Legislative Assembly General Elections 1969 of the States of Malaya, Sabah and Sarawak},
		author    = {Election Commission},
		year      = {1971},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge04report,
		title     = {Report on the Parliamentary (Dewan Rakyat) and State Legislative Assembly General Elections 1974 of the States of Malaya and Sarawak},
		author    = {Election Commission},
		year      = {1974},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge05report,
		title     = {Report on the General Elections to the House of Representatives and the State Legislative Assemblies Other Than the State Legislative Assemblies of Kelantan, Sabah and Sarawak 1978},
		author    = {Election Commission},
		year      = {1978},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge06report,
		title     = {Report on the Malaysian General Elections 1982},
		author    = {Election Commission},
		year      = {1982},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge07report,
		title     = {Report on the Malaysian General Elections 1986},
		author    = {Election Commission},
		year      = {1986},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge08report,
		title     = {Report on the Malaysian General Elections 1990},
		author    = {Election Commission},
		year      = {1990},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge09report,
		title     = {Report of the General Election Malaysia 1995},
		author    = {Election Commission},
		year      = {1995},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge10report,
		title     = {Report of the General Election Malaysia 1999},
		author    = {Election Commission},
		year      = {1999},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge11report,
		title     = {Report of the General Election Malaysia 2004},
		author    = {Election Commission},
		year      = {2004},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge12report,
		title     = {Report of the General Election Malaysia 2008},
		author    = {Election Commission},
		year      = {2008},
		publisher = {Election Commission of Malaysia},
	}

	@book{ge13report,
		title     = {Report of the General Election Malaysia 2013},
		author    = {Election Commission},
		year      = {2013},
		publisher = {Election Commission of Malaysia},
	}

	@book{sabah1967report,
		title     = {Report on the State Legislative Assembly General Election 1967 of the State of Sabah},
		author    = {Election Commission},
		year      = {1967},
		publisher = {Election Commission of Malaysia},
	}

	@book{sabah1971report,
		title     = {Report on the State Legislative Assembly General Election 1971 of the State of Sabah},
		author    = {Election Commission},
		year      = {1971},
		publisher = {Election Commission of Malaysia},
	}

	@book{sabah1976report,
		title     = {Report on the State Legislative Assembly General Election 1976 of the State of Sabah},
		author    = {Election Commission},
		year      = {1976},
		publisher = {Election Commission of Malaysia},
	}

	@book{kelantan1978report,
		title     = {Report on the State Legislative Assembly General Election 1978 of the State of Kelantan},
		author    = {Election Commission},
		year      = {1978},
		publisher = {Election Commission of Malaysia},
	}

	@book{sarawak1979report,
		title     = {Report on the State Legislative Assembly General Election 1979 of the State of Sarawak},
		author    = {Election Commission},
		year      = {1979},
		publisher = {Election Commission of Malaysia},
	}

	@book{sabah1981report,
		title     = {Report on the State Legislative Assembly General Election 1981 of the State of Sabah},
		author    = {Election Commission},
		year      = {1981},
		publisher = {Election Commission of Malaysia},
	}

	@book{sarawak1983report,
		title     = {Report on the State Legislative Assembly General Election 1983 of the State of Sarawak},
		author    = {Election Commission},
		year      = {1983},
		publisher = {Election Commission of Malaysia},
	}

	@book{sabah1985report,
		title     = {Report on the State Legislative Assembly General Election 1985 of the State of Sabah},
		author    = {Election Commission},
		year      = {1985},
		publisher = {Election Commission of Malaysia},
	}

	@book{sabah1986report,
		title     = {Report on the State Legislative Assembly General Election 1986 of the State of Sabah},
		author    = {Election Commission},
		year      = {1986},
		publisher = {Election Commission of Malaysia},
	}

	@book{sarawak1987report,
		title     = {Report on the State Legislative Assembly General Election 1987 of the State of Sarawak},
		author    = {Election Commission},
		year      = {1987},
		publisher = {Election Commission of Malaysia},
	}

	@book{sabah1990report,
		title     = {Report on the State Legislative Assembly General Election 1990 of the State of Sabah},
		author    = {Election Commission},
		year      = {1990},
		publisher = {Election Commission of Malaysia},
	}

	@book{sarawak1991report,
		title     = {Report on the State Legislative Assembly General Election 1991 of the State of Sarawak},
		author    = {Election Commission},
		year      = {1991},
		publisher = {Election Commission of Malaysia},
	}

	@book{sabah1994report,
		title     = {Report on the State Legislative Assembly General Election 1994 of the State of Sabah},
		author    = {Election Commission},
		year      = {1994},
		publisher = {Election Commission of Malaysia},
	}

	@book{sarawak1996report,
		title     = {Report on the State Legislative Assembly General Election 1996 of the State of Sarawak},
		author    = {Election Commission},
		year      = {1996},
		publisher = {Election Commission of Malaysia},
	}

	@book{sabah1999report,
		title     = {Report on the State Legislative Assembly General Election 1999 of the State of Sabah},
		author    = {Election Commission},
		year      = {1999},
		publisher = {Election Commission of Malaysia},
	}

	@book{sarawak2001report,
		title     = {Report on the State Legislative Assembly General Election 2001 of the State of Sarawak},
		author    = {Election Commission},
		year      = {2001},
		publisher = {Election Commission of Malaysia},
	}

	@book{sarawak2006report,
		title     = {Report on the State Legislative Assembly General Election 2006 of the State of Sarawak},
		author    = {Election Commission},
		year      = {2006},
		publisher = {Election Commission of Malaysia},
	}

	@book{means1991malaysia,
		author    = {Gordon P. Means},
		title     = {Malaysia: The Second Generation},
		publisher = {Oxford University Press},
		address   = {Singapore},
		year      = {1991}
	}

	@article{yusoff2001sabah,
		title={Sabah politics under {Pairin}},
		author={Yusoff, Mohammad Agus},
		journal={JATI - Journal of Southeast Asian Studies},
		volume={6},
		pages={29--48},
		year={2001}
	}

	@article{lee2020collapse,
		title={The Collapse of the State Government in {Sabah}: Back to the Drawing Board},
		author={Lee, P.O.},
		journal={ISEAS - Yusof Ishak Institute Commentaries},
		year={2020},
		note={Available at: \url{https://citethis.link/meco1-iseas}}
	}

	@incollection{junid2019battle,
		title={The battle for {Perak}},
		author={Junid, Iskandar Dzulkarnain Ahmad},
		booktitle={Malaysia's 14th General Election and {UMNO}'s Fall},
		pages={223--239},
		year={2019},
		publisher={Routledge}
	}

	@book{nohlen2001elections,
		title={Elections in Asia and the Pacific: A data handbook},
		author={Nohlen, Dieter and Grotz, Florian and Hartmann, Christof},
		volume={2},
		year={2001},
		publisher={Oxford University Press}
	}

	@book{loh2002democracy,
		title={Democracy in Malaysia: discourses and practices},
		author={Loh, Francis Kok-Wah and Khoo, Boo Teik},
		number={5},
		year={2002},
		publisher={Psychology Press}
	}

	@book{welsh2016elections,
		title={Elections in Malaysia},
		author={Welsh, Bridget},
		year={2016},
		publisher={Routledge Handbook of Contemporary Malaysia}
	}

	@incollection{hai2017electoral,
		title={Electoral campaigning in Malaysia},
		author={Hai, Lim Hong and Ming, Ong Kian},
		booktitle={Election Campaigning in East and Southeast Asia},
		pages={55--77},
		year={2017},
		publisher={Routledge}
	}

	@article{hackett2025redrawing,
		title={Redrawing Democracy: Quantifying House District Continuity and Change, 1789--2024},
		author={Hackett, Ursula},
		journal={Studies in American Political Development},
		pages={1--15},
		year={2025},
		publisher={Cambridge University Press}
	}

	@article{crespin2005using,
		title={Using geographic information systems to measure district change, 2000--2002},
		author={Crespin, Michael H},
		journal={Political Analysis},
		volume={13},
		number={3},
		pages={253--260},
		year={2005},
		publisher={Cambridge University Press}
	}

	@article{mcghee2017measuring,
		title={Measuring efficiency in redistricting},
		author={McGhee, Eric},
		journal={Election Law Journal: Rules, Politics, and Policy},
		volume={16},
		number={4},
		pages={417--442},
		year={2017},
		publisher={Mary Ann Liebert, Inc. 140 Huguenot Street, 3rd Floor New Rochelle, NY 10801 USA}
	}

\end{filecontents*}

\newpage

% this section generates reference
\begingroup
\raggedright
\linespread{1.1}
\small
\let\oldthebibliography\thebibliography
\bibliography{mybib}
\endgroup

\section*{Author Contributions}
TT conceived, designed, and carried out all aspects of this study, including data collection, data curation, analysis, and manuscript preparation.

\section*{Competing Interests}
The author declares no competing interests. The author is not affiliated with any political party, or any organisation which actively participates in or aims to influence the outcome of Malaysian elections.

\section*{Acknowledgements}
This work did not receive any specific funding. I thank Rosmadi Fauzi and Zulkanain Abdul Rahman for their helpful feedback and suggestions on the dataset and manuscript. I also gratefully acknowledge Nimesha Thevananthan for her assistance with data collection, Danesh Prakash Chacko of Tindak Malaysia for providing historical insights and filling data gaps (particularly for the Sabah state election in 1971), and the MyElectionData volunteers for their assistance with completion and validation of candidate UID harmonisation and candidate demographic data. Finally, I thank the EC for granting access to physical records of historical election results via \textit{Pusat Sumber SPR}.

\end{document}

### 2025-12-03 tex/manuscript-r1.tex
Freeze tex files
Fix: Missing admin sections

@@
+\stop % This is the originally submitted manuscript which should not be re-compiled.
+
 \documentclass[11pt]{article}
@@
 \linespread{1.25}
+\usepackage{marvosym}
 \usepackage{titlesec}
+
 \titlespacing\section{0pt}{0.21in}{0.03in}
@@
 			\Large
-			Thevesh Thevananthan\\[0.15in]  % ← Author name inserted here
+			Thevesh Thevananthan\footnotemark$^{\text{\Letter}}$\\[0.15in]
 		\end{center}
@@
 \end{center}
+
+\footnotetext[1]{Malaya University, W.P. Kuala Lumpur, Malaysia\\\Letter\space \href{mailto:thevesh.theva@gmail.com}{thevesh.theva@gmail.com}}
 
@@
 
+\section*{Data Availability}
+
+All datasets described in this paper are published on Harvard Dataverse\cite{meco_dataset} under a CC0 license.
+For convenience, the exact same datasets are also mirrored in repositories on Zenodo\cite{meco_codebase} and \href{https://github.com/Thevesh/paper-malaysian-election-corpus}{GitHub}.
+Both contain code and raw source files in addition to the datasets; I use GitHub to version-control active development and maintenance, with substantial updates released on Zenodo.
+
 \section*{Code Availability}
@@
 
-\newpage
-
 % this section generates reference
@@
 
+\section*{Acknowledgements}
+I thank Rosmadi Fauzi and Zulkanain Abdul Rahman for their helpful feedback and suggestions on the dataset and manuscript.
+I also gratefully acknowledge Nimesha Thevananthan for her assistance with data collection, Danesh Prakash Chacko of Tindak Malaysia for providing historical insights and filling data gaps (particularly for the Sabah state election in 1971), and the MyElectionData volunteers for their assistance with completion and validation of candidate UID harmonisation and candidate demographic data.
+Finally, I thank the EC for granting access to physical records of historical election results via \textit{Pusat Sumber SPR}.
+
 \section*{Author Contributions}
 TT conceived, designed, and carried out all aspects of this study, including data collection, data curation, analysis, and manuscript preparation.
+
+\section*{Funding}
+
+This work did not receive any specific funding.
 
@@
 
-\section*{Acknowledgements}
-This work did not receive any specific funding.
-I thank Rosmadi Fauzi and Zulkanain Abdul Rahman for their helpful feedback and suggestions on the dataset and manuscript.
-I also gratefully acknowledge Nimesha Thevananthan for her assistance with data collection, Danesh Prakash Chacko of Tindak Malaysia for providing historical insights and filling data gaps (particularly for the Sabah state election in 1971), and the MyElectionData volunteers for their assistance with completion and validation of candidate UID harmonisation and candidate demographic data.
-Finally, I thank the EC for granting access to physical records of historical election results via \textit{Pusat Sumber SPR}.
-
 \end{document}

### 2025-12-06 compile.py
Update: Sabah SE-15

@@ -115,16 +115,11 @@ def main():
         raise ValueError(f"Validation failed for {len(df[df.check != 0])} seats!")
 
     df = pd.read_parquet("src-data/consol_ballots.parquet")
-    for v in ["candidate", "party", "coalition"]:
+    for v in ["party", "coalition", "candidate"]:
         cf = pd.read_csv(f"src-data/lookup_{v}.csv")
         assert len(df[df[f"{v}_uid"].isin(cf[f"{v}_uid"])]) == len(
             df
         ), f"Missing {v} in lookup file!"
-
-    cf = pd.read_csv("src-data/lookup_seat.csv")
-    cf.date = pd.to_datetime(cf.date).dt.date
-    df = pd.merge(df, cf, on=["date", "election", "state", "seat"], how="left")
-    assert len(df[df.type.isnull()]) == 0, "Missing seat in lookup file!"
 
     print("Validation passed!")
 

### 2025-12-06 compile.py
Reorg datasets

@@ -123,20 +123,29 @@ def main():
 
     print("Validation passed!")
 
-    print("\n\n --------- Generating subsets ----------\n")
+    print("\n\n --------- Generating SFC files ----------\n")
 
     for v in ["ballots", "stats"]:
         df = pd.read_parquet(f"src-data/consol_{v}.parquet")
-        write_csv_parquet(f"src-data/federal_{v}", df[df.election.str.startswith("GE-")])
-        write_csv_parquet(f"src-data/byelection_{v}", df[df.election.str.startswith("BY-")])
+        write_csv_parquet(f"src-data/sfc/federal_{v}", df[df.election.str.startswith("GE-")])
+        write_csv_parquet(f"src-data/sfc/byelection_{v}", df[df.election.str.startswith("BY-")])
 
         for state, state_code in zip(get_states(my=0, codes=0), get_states(my=0, codes=1)):
             if "W.P." in state:
                 continue
             write_csv_parquet(
-                f"src-data/state_{state_code}_{v}",
+                f"src-data/sfc/state_{state_code}_{v}",
                 df[(df.state == state) & (df.election.str.startswith("SE-"))],
             )
+
+    print("\n\n --------- Generating lookup parquets ----------\n")
+
+    for v in ["candidate", "party", "coalition", "party_succession", "dates"]:
+        cf = pd.read_csv(f"src-data/lookup_{v}.csv")
+        for c in cf.columns:
+            if "date" in c:
+                cf[c] = pd.to_datetime(cf[c]).dt.date
+        write_csv_parquet(f"src-data/lookup_{v}", cf)
 
     print("\n\n --------- ✨✨✨ DONE ✨✨✨ ----------\n")  # Not AI; I like sparkles after success
 

### 2025-12-06 compile.py
Fix: Candidate lookup format

@@ -143,7 +143,7 @@ def main():
     for v in ["candidate", "party", "coalition", "party_succession", "dates"]:
         cf = pd.read_csv(f"src-data/lookup_{v}.csv")
         for c in cf.columns:
-            if "date" in c:
+            if c in ["date"]:
                 cf[c] = pd.to_datetime(cf[c]).dt.date
         write_csv_parquet(f"src-data/lookup_{v}", cf)
 

### 2025-12-15 tex/manuscript-final.tex
Prepare final manuscript

--- 2025-12-03 tex/manuscript-r1.tex
@@
-\stop % This is the originally submitted manuscript which should not be re-compiled.
-
 \documentclass[11pt]{article}
@@
 			\LARGE
-			The Malaysian Election Corpus (\acronymend):\\Federal and State-Level Election Results\\from 1955 to 2025 \\[0.21in]
+			The Malaysian Election Corpus (\acronymend):\\Federal and State-Level Election Results\\from 1955 to the Present \\[0.21in]
 			\Large
@@
 
-In this paper, I address this gap by providing the Malaysian Election Corpus (MECo),\cite{meco_dataset} the first comprehensive open database of Malaysian election results at the federal and state level.
+In this paper, I address this gap by providing the Malaysian Election Corpus (MECo),\cite{meco_dataset} the first complete open database of Malaysian election results at the federal and state level.
 MECo is intended as a living resource which provides the go-to empirical foundation for research and journalism on Malaysian elections.
-The database covers \textit{all} general elections since the pre-independence general election in 1955, and all \TOTALCONTESTSBYELEC\space by-elections since the 12th federal general election in 2008.
-In total, it records \UNIQUECANDIDATES\space unique candidates representing \TOTALPARTIES\space political parties in \TOTALCONTESTS\space unique electoral contests from 1955 to 2025.
+The database covers \textit{all} general elections and by-elections since the pre-independence general election in 1955.
+In total, it records \UNIQUECANDIDATES\space unique candidates representing \TOTALPARTIES\space political parties in \TOTALCONTESTS\space unique electoral contests from 1955 to the present.
 
@@
 I chose \texttt{ballots\_issued} as the variable to adjust for two reasons.
-First, until the 1989 amendment of the Elections (Conduct of Elections) Regulations 1981 (implemented at the 1989 federal general election), the number of unreturned ballots was not reported (and thus assumed to be 0).
+First, until the 1981 amendment of the Elections (Conduct of Elections) Regulations (implemented from the 1990 federal general election onwards), the number of unreturned ballots was not reported (and thus assumed to be 0).
 Second, because the number of rejected ballots is very small relative to the number of ballots issued, using rejected ballots as the adjusted variable would have resulted in a much larger correction in percentage terms -- specifically, the correction would have required a 20\% change to the number of rejected ballots on average (with several exceeding 50\%), relative to a 0.6\% change to the number of ballots issued (with only one above 5\%, and none above 20\%).

### 2025-12-28 tex/manuscript-final.tex
Final manuscript

@@
 % colors
-\usepackage{tcolorbox}
+\usepackage[most]{tcolorbox}
 \usepackage{color} % colors
@@
 \newcommand\ppspace {\\[0.14in]}
-\newcommand{\logsep}{\begin{center}---------------\end{center}}
+\newcommand{\logsep}{\begin{center}-----------------\end{center}}
 
@@
 	\begin{centering}
-
-		\vspace{1.2ex}
-		\begin{minipage}{0.8\linewidth}
-			\begin{tcolorbox}[boxsep = 3.3pt, boxrule=0.4pt, colback = white, colbacktitle=white, coltitle = black, colframe= black, title=\centering \textbf{#1}]
+		\begin{minipage}{1\linewidth}
+			\begin{tcolorbox}[boxsep = 3.3pt, boxrule=0.4pt, colback = black!4, colbacktitle=black!4, coltitle = black, colframe= black, title=\centering \textsc{#1}]
 				\centering
@@
 		\end{minipage}		
-		\vspace{1.2ex}
-
 	\end{centering}
@@
 \def\UNIQUECANDIDATES{14,000}
-\def\TOTALCORRECTIONS{115}
-
-\phantom{Thevesh}
+\def\TOTALCORRECTIONS{114}
+
+\highlight{Accepted for Publication}{
+	This version of the article has been peer-reviewed and accepted for publication in \textit{Scientific Data}.
+However, this is not the Version of Record and does not reflect post-acceptance improvements, or any corrections.
+The Version of Record is available at: \href{https://doi.org/10.1038/s41597-025-06502-7}{doi.org/10.1038/s41597-025-06502-7}
+}
 
@@
 			\LARGE
-			The Malaysian Election Corpus (\acronymend):\\Federal and State-Level Election Results\\from 1955 to the Present \\[0.21in]
+			The Malaysian Election Corpus (\acronymend):\\Federal and State-Level Election Results\\from 1955 to 2025\\[0.21in]
 			\Large
@@
 Similarly, international turnout or election integrity datasets\cite{icoma2023turnout,norris2014integrity} capture only high-level national indicators.
-Locally, a number of news and civil society organisations such as Tindak Malaysia\cite{tindak_data}, malaysiakini (\href{https://citethis.link/undinfo}{undi.info}), and Sinar Project compile election data to varying degrees of completeness and quality, but these efforts -- while laudable for their public service, and valuable as a stopgap measure -- typically lack proper data hygiene and standardisation, and are not subjected to systematic validation and review, thus limiting their usefulness for rigorous empirical research and long-term preservation.
+Locally, a number of news and civil society organisations such as Tindak Malaysia\cite{tindak_data}, malaysiakini (\href{https://citethis.link/undinfo}{undi.info}), and Sinar Project compile election data to varying degrees of completeness and quality, but these efforts---while laudable for their public service, and valuable as a stopgap measure---typically lack proper data hygiene and standardisation, and are not subjected to systematic validation and review, thus limiting their usefulness for rigorous empirical research and long-term preservation.
 
@@
 However, the EC's \href{https://citethis.link/spr-parties}{list of registered parties} does not distinguish between a single political party and a coalition of parties.
-For example, as of 30th October 2025, the list contains - without distinction - both the United Malays National Organisation (UMNO) as well as the Barisan Nasional (BN).
+For example, as of 30th October 2025, the list contains---without distinction---both the United Malays National Organisation (UMNO) as well as the Barisan Nasional (BN).
 The former is a `party' in the conventional sense, while the latter is actually a coalition of several parties, including UMNO itself.
@@
 Political parties which are part of stable coalitions often choose to contest under the coalitional identity.
-For example, UMNO - Malaysia's oldest political party - has never contested an election under its own banner, instead contesting under the Alliance flag until 1973, and the BN flag thereafter.
+For example, UMNO---Malaysia's oldest political party---has never contested an election under its own banner, instead contesting under the Alliance flag until 1973, and the BN flag thereafter.
 This renders it impossible to analyse the political trajectory of UMNO relative to other component parties (especially MIC and MCA) using official data.
@@
 For this reason, I made the methodological choice to capture 3 separate variables (see Data Records for complete schema).
-First, \texttt{party\_on\_ballot} - which faithfully captures the exact listing of the candidate on the official ballot.
-Second, \texttt{party} - which captures the true party allegiance of the candidate.
-Third, \texttt{coalition} - which captures the coalitional allegiance of the party.
-It was extremely difficult to consolidate this information going back to 1955, especially for state-level results which receive far less attention than federal results - however, I was able to eventually fill in all gaps using a combination of existing scholarly work,\cite{welsh2016elections, hai2017electoral, loh2002democracy, nohlen2001elections} media reports (for modern elections), archived news articles (for older elections), and consultation with colleagues specialising in election history.
+First, \texttt{party\_on\_ballot}---which faithfully captures the exact listing of the candidate on the official ballot.
+Second, \texttt{party}---which captures the true party allegiance of the candidate.
+Third, \texttt{coalition}---which captures the coalitional allegiance of the party.
+It was extremely difficult to consolidate this information going back to 1955, especially for state-level results which receive far less attention than federal results.
+However, I was able to eventually fill in all gaps using a combination of existing scholarly work,\cite{welsh2016elections, hai2017electoral, loh2002democracy, nohlen2001elections} media reports (for modern elections), archived news articles (for older elections), and consultation with colleagues specialising in election history.
 To the best of my knowledge, MECo is now the only publicly-available dataset with complete data allowing users to distinguish between the 3 dimensions of political allegiance captured here.
@@
 Candidate UIDs enable the accurate tracking of individual candidates across elections.
-Beyond the obvious use case of distinguishing candidates with the same name (e.g.\ the dataset contains 8 unique individuals with the exact same name - `Ahmad bin Abdullah'), robust candidate UIDs are particularly important in the Malaysian context, where candidates frequently acquire new honorifics, adopt different formatting conventions, or spell their name differently over time.
+Beyond the obvious use case of distinguishing candidates with the same name (e.g.\ the dataset contains 8 unique individuals with the exact same name---`Ahmad bin Abdullah'), robust candidate UIDs are particularly important in the Malaysian context, where candidates frequently acquire new honorifics, adopt different formatting conventions, or spell their name differently over time.
 Two illustrative examples demonstrate the need for candidate UIDs.
@@
 Where possible, these were verified against public records, particularly for recent elections.
-DOB were obtained through extensive manual searches across thousands of sources - including biographical directories, news archives, parliamentary profiles, and obituary notices - and recorded in ISO format (YYYY-MM-DD).
+DOB were obtained through extensive manual searches across thousands of sources---including biographical directories, news archives, parliamentary profiles, and obituary notices---and recorded in ISO format (YYYY-MM-DD).
 Reliable birth information could not be found for 33.2\% of candidates overall, reflecting limited public documentation in earlier decades.
@@
 In fact, it arguably merits dedicated scholarly handling, since electoral lineage has never been rigorously documented or studied in the Malaysian context.
-That having been said, users who wish to augment \acronym with other constituency-based datasets -- for example, the \href{https://citethis.link/opendosm-parlimen}{subnational statistics} published by the Department of Statistics Malaysia -- should rely on the intrinsic uniqueness of the \texttt{date-state-constituency} combination as a composite key.
+That having been said, users who wish to augment \acronym with other constituency-based datasets---for example, the \href{https://citethis.link/opendosm-parlimen}{subnational statistics} published by the Department of Statistics Malaysia---should rely on the intrinsic uniqueness of the \texttt{date-state-constituency} combination as a composite key.
 This avoids imposing any particular lineage model, while ensuring that external data can be merged cleanly and reproducibly.
@@
 
-This validation procedure also revealed \TOTALCORRECTIONS\space contests (excluding elections before 1960 which did not report $I$, and the 2006 Sarawak state general election, which did not report $I$, $U$, or $R$) for which the data was digitised accurately based on my source material, but which nevertheless failed to satisfy Equation (\ref{eq:validation}).
+This validation procedure also revealed \TOTALCORRECTIONS\space contests for which the data was digitised accurately based on my source material, but which nevertheless failed to satisfy Equation (\ref{eq:validation}).
 These errors presumably occurred due to mistakes in data entry which were not caught and corrected during the original publication process.
-In order to ensure a clean dataset, I applied a standard correction -- for all \TOTALCORRECTIONS\space contests failing validation, I adjusted the number of ballots issued (as documented in \texttt{corrections.csv}) such that Equation (\ref{eq:validation}) holds.
+In order to ensure a clean dataset, I applied a standard correction---for all \TOTALCORRECTIONS\space contests failing validation, I adjusted the number of ballots issued (as documented in \texttt{corrections.csv}) such that Equation (\ref{eq:validation}) holds.
 I chose \texttt{ballots\_issued} as the variable to adjust for two reasons.
-First, until the 1981 amendment of the Elections (Conduct of Elections) Regulations (implemented from the 1990 federal general election onwards), the number of unreturned ballots was not reported (and thus assumed to be 0).
-Second, because the number of rejected ballots is very small relative to the number of ballots issued, using rejected ballots as the adjusted variable would have resulted in a much larger correction in percentage terms -- specifically, the correction would have required a 20\% change to the number of rejected ballots on average (with several exceeding 50\%), relative to a 0.6\% change to the number of ballots issued (with only one above 5\%, and none above 20\%).
+First, until the 1981 amendment of the Elections (Conduct of Elections) Regulations (implemented fully from the 1990 federal general election onwards), the number of unreturned ballots was not reported (and thus assumed to be 0).
+Second, because the number of rejected ballots is very small relative to the number of ballots issued, using rejected ballots as the adjusted variable would have resulted in a much larger correction in percentage terms---specifically, the correction would have required a 20\% change to the number of rejected ballots on average (with several exceeding 50\%), relative to a 0.6\% change to the number of ballots issued (with only one above 5\%, and none above 20\%).
 
@@
 The Malaysian Election Corpus (\acronymend) is designed to support a wide range of use cases, ranging from rigorous empirical research to rapid data journalism, and even casual civic technology projects.
-In the academic realm, \acronym -- as the first database of its kind for Malaysia -- serves as a foundational resource for research in electoral studies, political science, and public policy.
+In the academic realm, \acronym---as the first database of its kind for Malaysia---serves as a foundational resource for research in electoral studies, political science, and public policy.
 Researchers can employ the data to answer important questions about the evolution of Malaysia's electoral system, employing both cross-sectional and longitudinal analysis.
@@
 In addition to making the data accessible to non-technical users, the site is intended to serve as the primary channel for continuous updates and enhancements.
-Future improvements to \acronym will be reflected on the site as new versions (and the corresponding source code) are archived on Harvard Dataverse\cite{meco_dataset} and Zenodo\cite{meco_codebase}, ensuring that users always have easy access to the freshest data.
+Future improvements to \acronym will be reflected on the site as new versions are archived on Harvard Dataverse\cite{meco_dataset} and Zenodo\cite{meco_codebase}, ensuring that users always have the freshest data.
 
@@
 \begin{enumbul}
-	\item \texttt{compile.py}, which generates and validates all tabular datasets published on Harvard Dataverse, with the exception of the \texttt{lookup*.csv} files, which were manually curated.
+	\item \texttt{compile.py}, which generates and validates all tabular datasets, with the exception of the \texttt{lookup*.csv} files, which were manually curated.
 	\item \texttt{dataviz.py}, which generates all visualisations used in this paper.
@@
 		author      = {Thevananthan, Thevesh},
-		title       = {{The Malaysian Election Corpus}: Federal and State-Level Election Results since 1955},
+		title       = {{The Malaysian Election Corpus}: Federal and State-Level Election Results since 1955, v5},
 		year        = {2025},
@@
 I thank Rosmadi Fauzi and Zulkanain Abdul Rahman for their helpful feedback and suggestions on the dataset and manuscript.
-I also gratefully acknowledge Nimesha Thevananthan for her assistance with data collection, Danesh Prakash Chacko of Tindak Malaysia for providing historical insights and filling data gaps (particularly for the Sabah state election in 1971), and the MyElectionData volunteers for their assistance with completion and validation of candidate UID harmonisation and candidate demographic data.
-Finally, I thank the EC for granting access to physical records of historical election results via \textit{Pusat Sumber SPR}.
-
-\section*{Author Contributions}
-TT conceived, designed, and carried out all aspects of this study, including data collection, data curation, analysis, and manuscript preparation.
+I also gratefully acknowledge Nimesha Thevananthan for her assistance with data collection, Danesh Prakash Chacko of Tindak Malaysia for providing historical insights and filling data gaps, and the MyElectionData volunteers for their assistance with completion and validation of candidate UID harmonisation and candidate demographic data.
+Finally, I thank the EC for granting access to physical election reports via \textit{Pusat Sumber SPR}.
+
+\section*{Author Contributions (CRediT statement)}
+TT: Conceptualization, Methodology, Software, Validation, Formal analysis, Investigation, Resources, Data curation, Writing - original draft, Writing - review and editing, Visualization, Supervision, Project administration.
 
@@
 \section*{Competing Interests}
-The author declares no competing interests.
-The author is not affiliated with any political party, or any organisation which actively participates in or aims to influence the outcome of Malaysian elections.
+The author declares no competing interests. The author is not affiliated with any political party or election-based organisation.
 
